\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\usepackage{hyperref,cleveref}
\renewcommand{\familydefault}{ppl}
\newcommand{\curl}{\text{curl}}
\newcommand{\diverg}{\text{div}}
\newcommand{\tr}{\text{tr}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\disc}{disc}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}
\newcommand{\fraccomma}{\genfrac{}{}{0pt}{}{}{,}}
\definecolor{wikipediadarkblue}{rgb}{0.023, 0.270, 0.676}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=blue,
    urlcolor=red
}

% \hypersetup{
%     urlbordercolor={1 0 0}, % Red box for URLs
%     linkbordercolor=blue, % Blue box for internal links
%     % the values are in RGB format from 0 to 1
% }


\input{hui_r.tex}

\title{Complex Analysis Qualifying Exam Review
\\ 
\vspace{0.4cm}
\large Spring 2026}



% \author{(Please email hsun95@jh.edu if you see typos)}
% \date{\today}


\begin{document}

\maketitle

\tableofcontents
\newpage



\chapter{Basic calculus in the complex domain}

\begin{prop}[Cauchy-Riemann Equations]
    If $f:\Omega\to\C$ is holomorphic, then $\frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}$ exist and are continuous on $\Omega$, and 
    \begin{equation*}
        \frac{\partial f}{\partial x}=\frac{1}{i}\frac{\partial f}{\partial y}
    \end{equation*}
    If we write $f=u+iv$, then the above is equivalent to 
    \begin{equation*}
        \begin{cases}
            \frac{\partial u}{\partial x}=\frac{\partial v}{\partial y}\\
            \frac{\partial v}{\partial x}=-\frac{\partial u}{\partial y}
        \end{cases}
    \end{equation*}
\end{prop}

\begin{prop}[Converse of Cauchy-Riemann]
    If $f:\Omega\to\C$ is $C^1$ and satisfies Cauchy-Riemann equations, then $f$ is holomorphic.
\end{prop}

\begin{prop}
    If $f:\overline{\Omega}\to\C$ is holomorphic, where $z_0\in\Omega$ and $D_r(z_0)\subset\Omega$, then for $z\in D_r(z_0)$, $f$ is given by a convergent power series 
    \begin{equation*}
        f(z)=\sum_{k=0}^\infty a_k(z-z_0)^k
    \end{equation*}
    where 
    \begin{equation*}
        a_k=\frac{1}{2\pi i}\int_{\partial\Omega}\frac{f(\zeta)}{(\zeta-z_0)^{k+1}}d\zeta=\frac{f^{(k)}(z_0)}{k!}
    \end{equation*}
\end{prop}
(This follows from Cauchy integral formula).


% \begin{defn}[complex log]
%     The logorithmic function extended to the complex plane is $\log:\C\setminus\R^-\to\C$, given by 
%     \begin{equation*}
%         \log z=\frac{1}{z}\frac{1}{\zeta}d\zeta
%     \end{equation*}
% \end{defn}


\begin{thm}
    Let $f:\Omega\to\C$ be holomorphic, where $\Omega$ is open. Let $p\in\Omega$, assume $f'(p)\neq 0$. Then there exists a neighborhood $O$ of $p$ and a neighborhood $U$ of $q=f(p)$ such that $f:O\to U$ is bijective, where the inverse $g=f^{-1}: U\to O$ is holomorphic. For $z\in O, w=f(z)$, we have 
    \begin{equation*}
        g'(w)=\frac{1}{f'(z)}
    \end{equation*}
\end{thm}


\begin{prop}
    Suppose $\Omega\subset\C$ is convex. Assume $f$ is holomorphic in $\Omega$ and there exists $a\in\C$ such that 
    \begin{equation*}
        \text{Re } af'>0 \text{ on } \Omega
    \end{equation*}
    then $f$ is one-to-one onto its image $f(\Omega)$.
\end{prop}


\begin{defn}
    square roots, complex logs
\end{defn}


\chapter{Cauchy integral theorem}

\begin{thm}
    If $f\in C^1(\overline{\Omega})$ is holomorphic on $\Omega$, then 
    \begin{equation*}
        \int_{\partial\Omega}f(z)dz=0
    \end{equation*}
\end{thm}

\begin{thm}
    If $f\in C^1(\overline{\Omega})$ is holomorphic on $\Omega$ and $z_0\in\Omega$, then 
    \begin{equation*}
        f(z_0)=\frac{1}{2\pi i}\int_{\partial\Omega}\frac{f(z)}{z-z_0}dz
    \end{equation*}
    One can change $\partial\Omega$ to an simple closed curve $\gamma$ completely contained in $\Omega$.
\end{thm}

\begin{prop}
    If $f$ is holomorphic on an open set $\Omega\subset\C$, then 
    \begin{equation*}
        f\in C^\infty(\Omega)
    \end{equation*}
\end{prop}


\begin{thm}[holomorphic implies analytic]
    If $f\in C^1(\overline{\Omega})$ is holomorphic, then for $z\in D_r(z_0)\subset\Omega$, then $f(z)$ has the convergent power series expansion 
    \begin{equation*}
        f(z)=\sum_{n=0}^\infty a_n(z-z_0)^n
    \end{equation*}
    where 
    \begin{equation*}
        a_n=\frac{1}{2\pi i}\int_{\partial\Omega}\frac{f(\zeta)}{(\zeta-z_0)^{n+1}}d\zeta=\frac{f^{(n)}(z_0)}{n!}
    \end{equation*}
\end{thm}

\begin{prop}
    Let $\Omega\subset\C$ be an open set and let $f_\nu:\Omega\to\C$ be holomorphic. Assume $f_\nu\to f$ locally uniformly, then $f:\Omega\to\C$ is holomorphic and $f_\nu'\to f'$ locally uniformly on $\Omega$.
\end{prop} 


\begin{prop}[maximum principle]
    Let $\Omega\subset\C$ be connected, open. If $f$ is holomorphic in $\Omega$, then for $z_0\in\Omega$,
    \begin{equation*}
        \text{ if } |f(z_0)|=\sup_{z\in\Omega}|f(z)|, \text{ then } f \text{ is constant on $\Omega$}
    \end{equation*}
    Moreover, if $\Omega$ is bounded and $f\in C(\overline{\Omega})$, then 
    \begin{equation*}
        \sup_{z\in\overline{\Omega}}|f(z)|=\sup_{z\in\partial\Omega}|f(z)|
    \end{equation*}
    (In this case, $f$ must attain a maximum in $\overline{\Omega}$). This basically states that either $f$ is constant or $f$ attains maximum on the boundary.
\end{prop}


\begin{prop}
    Suppose $f$ is holomorphic on the unit disk $D_1(0)$. Assume $|f(z)|\leq 1$ for $|z|<1$, and $f(0)=0$. Then 
    \begin{equation*}
        |f(z)|\leq |z|
    \end{equation*}
    Moreover, $|f(z)|=|z|$ iff $f(z)=cz$ for some $c$ such that $|c|=1$.
\end{prop}

\begin{thm}[Liouville's theorem]
    If $f:\C\to\C$ is holomorphic and bounded, then $f$ is constant.
\end{thm}

A consequence of Liouville's theorem is the fundamental theorem of algebra:
\begin{prop}
    If $p(z)$ is a polynomial of degree $n\geq 1$, then $p(z)$ has at least one root. (Proof: consider $1/p(z)$).
\end{prop}

There are several properties that also hold for harmonic functions.
\begin{prop}[mean value property of harmonic functions]
    If $u\in C^2(\Omega)$ is harmonic, $z_0\in\Omega$, and $\overline{D_r(z_0)}\subset\Omega$, then 
    \begin{equation*}
        u(z_0)=\frac{1}{2\pi}\int_0^{2\pi}u(z_0+re^{i\theta})d\theta
    \end{equation*}
\end{prop}


\begin{prop}
    Let $\Omega\subset\C$ be connected and open. If $u:\Omega\to\R$ is harmonic in $\Omega$, then for $z_0\in\Omega$,
    \begin{equation*}
        u(z_0)=\sup_{z\in\Omega}u(z)\Rightarrow u \text{ is constnat on $\Omega$}
    \end{equation*}
    Moreover, if $\Omega$ is bounded, $u\in C(\overline{\Omega})$, then 
    \begin{equation*}
        \sup_{z\in\overline{\Omega}}u(z)=\sup_{z\in\partial\Omega}u(z)
    \end{equation*}
\end{prop}

\begin{prop}[Liouville for harmonic functions]
    If $u\in C^2(\C)$ is bounded and harmonic on all of $\C$, then $u$ is constant.
\end{prop}

\begin{prop}
    Let $\Omega\subset\C$ be simply connected domain. Then each harmonic function $u\in C^2(\Omega)$ has a harmonic conjugate.
\end{prop}

Next is a converse of Cauchy's integral theorem.
\begin{thm}[Morera's theorem]
    Let $g:\Omega\to\C$ be continuous, and 
    \begin{equation*}
        \int_\gamma g(z)dz=0
    \end{equation*}
    for any $\gamma=\partial R$, where $R\subset\Omega$ is a rectangle. Then $g$ is holomorphic.
\end{thm}


\begin{thm}[Schwarz reflection principle]
    Assume $f:\Omega^+\cup L\to\C$ is continuous, holomorphic in $\Omega^+$, and real-valued on $L$. Define $g:\Omega\to\C$ by
    \begin{equation*}
        g(z)=f(z), z\in\Omega^+\cup L, \overline{f(\overline{z})}, z\in\Omega^-
    \end{equation*}
    Then $g$ is holomorphic on $\Omega$.
\end{thm}


\begin{thm}[Goursat's theorem]
    If $f:\Omega\to\C$ is complex-differentiable at each point of $\Omega$, then $f$ is holomorphic.
\end{thm}



\begin{prop}[analytic continuation]
    Let $\Omega \subset \mathbb{C}$ be open and connected, and let $f : \Omega \to \mathbb{C}$ be holomorphic. If $f = 0$ on a set $S \subset \Omega$ and $S$ has an accumulation point $p \in \Omega$, then $f = 0$ on $\Omega$.

    In other words, if $f=g$ on a set $S\subset\Omega$, where $S$ contains an accumulation point, then $f=g$ on $\Omega$.
\end{prop}



% \begin{prop}
%     Let $\Omega \subset \mathbb{C}$ be a simply connected domain. Assume $f : \Omega \to \mathbb{C}$ is holomorphic and nowhere vanishing. Then there exists a holomorphic function $g$ on $\Omega$ such that
%     \begin{equation*}
%         e^{g(z)} = f(z), \quad \forall z \in \Omega.
%         \end{equation*}
% \end{prop}


\begin{defn}[singularities]
    There are three types of singularities: $p$ is said to be the following for $f:U\to\C$,
    \begin{enumerate}
        \item Removable: if there exists $\tilde{f}$ on $U$ such that $\tilde{f}=f$ on $U\setminus p$.
        \item Pole: if $|f(z)|\to\infty$ as $z\to p$. Equivalently, $p$ is a removable singularity for $1/f$.
        \item Essential singularity: not removable, not pole, an isolated singularity. $f(z)=e^{1/z}$.
    \end{enumerate}
\end{defn}


\begin{thm}
    If $p\in\Omega$ and $f$ is holomorphic on $\Omega\setminus p$ and bounded, then $p$ is a removable singularity.
\end{thm}

\begin{prop}
    If $f$ is holomorphic on $\Omega\setminus p$ with a pole at $p$, then there exists $k\in\mathbb{Z}^+$ such that 
    \begin{equation*}
        f(z)=\frac{F(z)}{(z-p)^k}
    \end{equation*}
    on $\Omega\setminus p$, where $F$ is holomorphic on $\Omega$ and $F(p)\neq 0$.
\end{prop}


\begin{prop}
    Suppose $f:\Omega\setminus p\to\C$ has an essential singularity at $p$. Then for any neighborhood of $U$ of $p$ in $\Omega$, the image of $U\setminus p$ is dense in $\C$.
\end{prop}


\begin{prop}
    If $f:\C\to\C$ is holomorphic and $|f(z)|\to\infty$ as $|z|\to\infty$, then $f(z)$ is a polynomial.
\end{prop}

\begin{prop}
    Let $f:\mathcal{A}\to\C$ be holomorphic, where the annulus $\mathcal{A}=\{z: r_0\leq |z-z_0|\leq r_1\}$, then $f$ is given by 
    \begin{equation*}
        f(z)=\sum_{n=-\infty}^\infty a_n(z-z_0)^n, z\in\mathcal{A} \tag{\text{Laurent series}}
    \end{equation*}
    and 
    \begin{equation*}
        a_n=\frac{1}{2\pi i}\int_\gamma \frac{f(\zeta)}{(\zeta-z_0)^{n+1}}d\zeta, n\in\mathbb{Z}
    \end{equation*}
    where $\gamma$ is any counterclockwise circle centered at $z_0$, of radius $r\in(r_0,r_1)$. 
\end{prop}



How does the Laurent series expansion help us?
\begin{prop}
    Suppose $f$ is holomorphic on $D_R(z_0)\setminus z_0$, with the above Laurent series. $f$ has a pole at $z_0$ iff $a_n=0$ for all but finitely many $n<0$; $f$ 
\end{prop}


\chapter{Fourier analysis and complex function theory}







\chapter{Useful facts}
\begin{enumerate}
    \item $e^z$ has the following power series expansion: 
    \begin{equation*}
        e^z=\sum_{j=0}^\infty\frac{z^j}{j!}
    \end{equation*}
    \item $\cos, \sin$ has the following power series expansions:
    \begin{equation*}
        \cos z=
    \end{equation*}
    \begin{equation*}
        \sin z=
    \end{equation*}
\end{enumerate}






\end{document}