\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\renewcommand{\familydefault}{ppl}
\newcommand{\tr}{\text{tr}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}


\input{hui.tex}

\title{Columbia HW Problems}

\date{\today}
\author{Hui Sun}


\begin{document}

\maketitle

\tableofcontents
\newpage

\chapter{HW2}

\begin{prob}[1]
    Determine whether the following statements are true or false. Justify your answers.

\begin{enumerate}
    \item[(a)] Any subring of a field is an integral domain.
    
    \item[(b)] The ring \(\mathbb{Z}/49\mathbb{Z}\) is an integral domain.
    
    \item[(c)] The direct product \(F_1 \times F_2\) of two fields is a field.
    
    \item[(d)] An element \(ab\) of a ring \(R\) is invertible if and only if both \(a\) and \(b\) are invertible.
    
    \item[(e)] The ring \(\mathbb{Z} \times \mathbb{Z}\) has exactly four idempotents. 
    \begin{itemize}
        \item[\textit{Hint}:] First find all idempotents in the ring \(\mathbb{Z}\). An idempotent is an element \(e\) such that \(e^2 = e\).
    \end{itemize}
\end{enumerate}
\end{prob}
\begin{proof}
    (a) True (b) False (c) False, consider $(1,0)\cdot (0,1)$ (d) False Consider $5+5=1$ in $\Z/6\Z$ (e) True.
\end{proof}

\begin{prob}[6]
    \begin{enumerate}
        \item[6.] An element \( x \) of a ring \( R \) is called \textit{nilpotent} if \( x^n = 0 \) for some \( n > 0 \). Note that \( 0 \in R \) is always nilpotent. (Remark: A nonzero nilpotent element is a zero divisor, while a zero divisor does not have to be nilpotent.)
        
        \begin{enumerate}
            \item[(a)] (5 points) Show that \( 0 \) is the only nilpotent element of an integral domain \( R \).
            
            \item[(b)] (5 points) Find all nilpotent elements in the following rings:
            \[
            \mathbb{Z}, \quad \mathbb{Q}, \quad \mathbb{Z}/9\mathbb{Z}, \quad \mathbb{Z}/12\mathbb{Z}, \quad \mathbb{Q}[x].
            \]
            
            \item[(c)] (optional, 10 points) Show that if \( x, y \) are nilpotent then \( x + y \) is nilpotent (assume that \( x^n = 0 \), \( y^m = 0 \), use that the ring is commutative and apply the binomial theorem from lecture 1 to some large power of \( x + y \)).
        \end{enumerate}
    \end{enumerate}    
\end{prob}
\begin{proof}
    \begin{prop}
        If $a\in\Z/n\Z$ is nilpotent, then $a$ is nilpotent in $\Z/d\Z$ for all divisors $d$ of $n$. Moreover, units are not nilpotent.
    \end{prop}
    (b) For $\Z/9\Z$: $\{0,3,6\}$ are nilpotents. For $\Z/12\Z$: $\{0, 6\}$ are nilpotents. (c) try $(x+y)^{m+n}$.
\end{proof}

\begin{prop}
    An integral domain must have characteristic $0$ or equal to some prime $p$; however, there exists char prime ring that is not an integral domain: $\Z/p\Z\times\Z/p\Z$.
\end{prop}



\chapter{HW3}


\begin{prob}[Q7]
    Let \( e \in R \) be an idempotent (i.e., \( e^2 = e \)) in a commutative ring \( R \).

\begin{enumerate}
    \item[(a)] Check that \( Re \) and \( R(1 - e) \) are ideals of \( R \) and that their intersection \( Re \cap R(1 - e) = 0 \). Show that any element \( a \in R \) has a unique presentation as a sum of an element in \( Re \) and an element in \( R(1 - e) \).

    \item[(b)] Prove that \( Re \) is a ring, with identity \( e \) and addition and multiplication inherited from \( R \). Likewise for \( R(1 - e) \). (Since \( 1 - e \) is also an idempotent, you don't need to repeat your arguments twice.)

    \item[(c)] Show that the map \( \phi: Re \times R(1 - e) \to R \) defined by \( \phi(a, b) = a + b \) is an isomorphism of rings.
\end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item[(a)] Let $a=re=r'(1-e)$, then 
        \begin{equation*}
            a=re=r'-r'e=r'e-r'e=0
        \end{equation*}
        Clearly we have $a=ae+a(1-e)$, and one can show this presentation is unique.
        \item[(b)] True.
        \item[(c)] It is surjective and injective both by part (a). 
    \end{enumerate}
    \begin{prop}
        Let $e\in R$ be a nontrivial idempotent, then viewing $Re, R(1-e)$ as rings with identities $e, (1-e)$, we can decompose $R$ into a product of two rings:
        \begin{equation*}
            R\cong Re\cong R(1-e)
        \end{equation*}
    \end{prop}
\end{proof}


\chapter{HW4}

\begin{prob}
    Compute the following sums and intersections of ideals in \(\mathbb{Q}[x]\) (first recall the relation between sums and intersections of ideals in \(F[x]\) to gcd and lcm of polynomials). Note that all the ideals of \(\mathbb{Q}[x]\) are principal. For each ideal, list the monic polynomial which generates the ideal.

    \[
    (x) + (x + 2), \quad (x^2) + (2x), \quad (3x^2 + 2x) + (4x^2 + x),
    \]
    \[
    (3x^2 + x + 5) + (0), \quad (x) \cap (2x + 1), \quad (2x) \cap (3x^2).
    \]
\end{prob}
\begin{proof}
    $(1), (x), (x), (3x^2+x+5), (x(2x+1)), (6x^2)=(x^2)$.
\end{proof}
\begin{prop}
    For the sum and intersection of ideals, we have
    \begin{equation*}
        (f)+(g)=(\gcd(f,g)), \quad (f)\cap (g)=(\text{lcm}(f,g))
    \end{equation*}
\end{prop}

\begin{prob}
    Consider the ring \( R = \mathbb{F}_p[x]/(f(x)) \), where \( f(x) \) is a polynomial of degree \( n \). Show that \( R \) is a finite ring with \( p^n \) elements.
\end{prob}
\begin{proof}
    Every $g(x)\in R$ is identified with its remainder by $f(x)$, where $\deg(r)<n$, hence $R$ consists of elements of the form 
    \begin{equation*}
        a_{n-1}x^n+\dots+a_1x+a_0
    \end{equation*}
    There are $p$ choices for each $a_i$, therefore this ring has size $p^n$.
\end{proof}



\begin{prob}
    Explain how to construct an infinite field of characteristic \( p \).
\end{prob}
\begin{proof}
    Start with $\F_p[x]$ it is not a field, so 
    \begin{equation*}
        \F_p(x)=\left\{\frac{p(x)}{q(x)}: q\neq 0\right\}
    \end{equation*}
    is an infinite field of characteristic $p$.
\end{proof}

\end{document}