\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\renewcommand{\familydefault}{ppl}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}


\input{hui.tex}

\title{Questions}




\date{\today}
\author{Hui Sun}


\begin{document}

\maketitle



\begin{prob}
    To see whether a polynomial is irreducible over $\Q$, is it sufficient to test whether $f\mod p$ is irreducible over any prime $p$?

    For example, $x^5-5x^3+1$.
\end{prob}
\begin{proof}
    Yes. The converse is not true, consider the minimal polynomial for $\sqrt{2}+\sqrt{3}$.
\end{proof}


\begin{prob}
    In the above example, how do we know that the Galois group contains an element of order $5$? (It is clear why it contains a transposition because there exists complex roots).
\end{prob}
\begin{proof}
    This is because the Galois group $G$ acts transitively on the set of roots, by the Orbit stabilizer theorem, we know 
    \begin{equation*}
        |G|=|\text{Orbit}(\alpha)|\cdot|\text{Stab}(\alpha)|=5\cdot|\text{Stab}(\alpha)|
    \end{equation*}
    i.e., $5$ divides $|G|$. By Cauchy's theorem, there exists an element of order $5$ in $G$, i.e., a $5$-cycle.
\end{proof}

\begin{prob}
    The Galois action on the set of roots implies for any root $r$ of the irreducible polynomial (where $G$ is the splitting field of), we must have 
    \begin{equation*}
        \text{Orbit}(r)=\{\text{ set of all roots}\}
    \end{equation*}
\end{prob}
\begin{proof}
    Yes, by defiition of a transitive action.
\end{proof}


\begin{prob}
    Is it true that if $I,J$ are ideals of a ring $R$, then 
    \begin{equation*}
        \frac{R}{I}\otimes_R\frac{R}{J}=\frac{R}{(I+J)}
    \end{equation*}
    in the case where $R=\Q[x]$, and $I,J$ are irreducible polynomials, we have 
    \begin{equation*}
        \frac{R}{(f)}\otimes_R\frac{R}{(g)}=\frac{R}{(f)+(g)}=\frac{R}{\gcd(f,g)}
    \end{equation*}
\end{prob}






\begin{prob}
    Fall 2014 Q2, $\text{Hom}_R(M,N)$.
\end{prob}





\begin{prob}
    $\Z/55\Z$.
\end{prob}
\begin{proof}
    We have $n_{11}=1$, and we can write $G$ as a semidirect product 
    \begin{equation*}
        G=\frac{\Z}{11\Z}\rtimes_\theta \frac{\Z}{5\Z}
    \end{equation*}
    where $\theta: \frac{\Z}{5\Z}\to\left(\frac{\Z}{11\Z}\right)^\times$. We know $\theta(1)$ needs to be sent to an elemennt of order $5$, which includes $3,4$.
    \begin{equation*}
        G=\la g,h: g^{11}=h^5=e, hgh^{-1}=g^3\ra
    \end{equation*}
    and 
    \begin{equation*}
        G=\la g,h: g^{11}=h^5=e, hgh^{-1}=g^4\ra
    \end{equation*}

\end{proof}


\begin{prob}
    Is cyclotomic extension cyclic.
\end{prob}
\begin{proof}
    No, consider $\Q(\zeta_8)$, then the Galois group is $\Z/2\Z\times\Z/2\Z$.
\end{proof}

\begin{prob}
    If an intermediate field extension of a Galois extension has order $a$, $k\subset E\subset K$ has $[E:k]=a$, then the subgroup that fixes $E$ has index $a$. 
\end{prob}

\begin{prob}
    Find all intermediate fields when the Galois group is $\Q(\zeta_9)$.
\end{prob}

\begin{prob}
    Find all the intermediate fields when the Galois group is $D_8$.
\end{prob}



\begin{prob}
    S2013-Q6(b)(c), S2016-Q3
\end{prob}


\begin{prob}
    Solvable by radicals, f2014-Q1 (polynomial), f2006-Q2 (field)
\end{prob}

\begin{prob}
    F2010-Q3
\end{prob}

\begin{prob}
    Review orbit-stabilizer theorem.
\end{prob}


\begin{prob}
    Map $S_4$ onto $S_3$ first for the irreducible rep.
\end{prob}
\begin{proof}
    Can only do it for the $2$ dimensional irred character.
\end{proof}

\begin{prob}
    Relationship between abelianization and $z(G)$. Why is $p^3$ nonabelian group has $[G,G]=p$. 
\end{prob}
\begin{proof}
    Find the smallest normal subgroup $H$ such that $G/H$ is abelian. The smallest in this case is $Z(G)$.
\end{proof}




\begin{prob}
    Irreducible rep of a cyclic group over $\R$ is $\leq 2$.
\end{prob}
\begin{proof}
    
\end{proof}

\begin{prob}
    Schur's lemma on simple modules over a semisimple ring. 
    \begin{equation*}
        \text{End}_A(S)\cong\C
    \end{equation*}
    where $S$ is a simple module. also like, irreducible, simple.
\end{prob}

\begin{prob}
    S2003-Q3, S2011-Q4
\end{prob}

% \begin{prob}
%     Some use $G/Z(G)$ to find the one-dim irreducible reps, for example, $A_4, D_4, S_4$.
% \end{prob}

% \begin{prop


\begin{prob}
    Isomorphism class of groups of order 360, page 238 aluffi.
\end{prob}


\begin{prob}
    Can I write all free $R$-modules as $R^n$
\end{prob}


\begin{prob}
    columns of the character table, sums of squares is $|G|/[(c)]$ ?
\end{prob}


\begin{prob}
    $\frac{K[t]}{(f(t))}$ is simple? is equal to $k(\alpha)$ for some $\alpha$ s.t. $f(\alpha)=0$.
\end{prob}



\begin{prob}
    since ext $k(\alpha)$ always factors over $k$? is $k(\alpha)$ be the splitting field for all $\alpha$ s.t. $f(\alpha)=0$ is a root? no. nononono.
\end{prob}

\begin{prob}
    Theorem 5.1
\end{prob}
\begin{prob}
    $x^4+1$ is reducible over all $\F_p$ for any $p$
\end{prob}

\begin{prob}
    relationship between $D_n, A_n$, galois
\end{prob}


\begin{prob}
    Degree $p$ irred polynomial, what is the degree of the splitting field? $p!$?
\end{prob}

\newpage
\begin{prob}
    normal basis theorem: connection w galois theory and linear alg
\end{prob}



\chapter{Aluffi}

Chapter VII: Fields.


Section 1: 5, 11, 14, 23

not done yet: 5





\chapter{Random Facts}

\begin{prop}
    If $R\subset F$ is a subring of a field, then $R$ is an integal domain. Moreover, if $k\subset R\subset F$ where $F/k$ is an algebraic extension, then $R$ is a subfield.
\end{prop}

\begin{prop}
    $\F_4$ embeds into $\F_{16}$, more generally, if the order allows (as a vector space over $\F_2$), then it embeds.
\end{prop}

\begin{prop}
    $\F_8/\F_2$ is a Galois extension and the Galois group is generated by the Frobenius transformation $\sigma: a\mapsto a^2$, $\{e, \sigma, \sigma^2\}$.

    Recall the equivalent defn of Galois: let $k\subset E$ be a field extension, if $[E: k]=|\text{Aut}_k(E)|$, then the extension is Galois.
\end{prop}

\begin{prop}
    You tend to forget Cayley--Hamilton. Let $p$ be the characteristic polynomial of some linear transformation $T$, then 
    \begin{equation*}
        p(T)=0
    \end{equation*}
\end{prop}


\begin{prop}
    Let $I,J\subset R$ be ideals, then 
    \begin{equation*}
        J+I\subset R/I
    \end{equation*}
    is also an ideal. For example, one could use this to show that if $R$ is Noetherian, then $R/I$ is also Noetherian.
\end{prop}


\begin{prop}
    Let $V$ be a finite dimensional vector space, let $T,S: V\to V$ be diagonalizable operators, if 
    \begin{equation*}
        TS=ST
    \end{equation*}
    then $T,S$ can be simultaneously diagonalized: in other words, $V$ has a basis containing eigenvectors of both $T$ and $S$.
\end{prop}


\begin{prop}
    Every ideal/element in a nonzero ring is contained in some maximal ideal $\mathfrak{m}$.
\end{prop}

\begin{prop}
    Each group has two interesting actions on itself: left-multiplcation and conjugation. Try both if needed!
\end{prop}

\begin{prop}
    Let $G$ be a group. Suppose that there is an integer $n$ and a subgroup $H\subseteq G$ such that $H$ is the only subgroup of $G$ with order $n$. Then $H$ is a normal subgroup of $G$.
\end{prop}

\begin{prop}
    Let $G$ be a finite group. Suppose that $H\subseteq G$ is a nonempty subset closed under the group operation. Then $H$ is a subgroup of $G$.
\end{prop}


\begin{prop}
    Simple abelian groups are cyclic $p$-groups.
\end{prop}

\begin{prop}
    If you want to prove anything about $R/I$, $G/H$, remember there is a one-to-one correspondence between ideals (subgroups) of $R/I$ ($G/H$) and ideals $J\subset R$ containing $I$ (subgroups of $G$ containing $H$.).
\end{prop}


\begin{prop}
    Let $\rho$ be an irreducible representation of $D_n$, then $\dim(\rho)\leq 2$ (Frobenius transofrmation).
\end{prop}




\end{document}