\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\renewcommand{\familydefault}{ppl}
\newcommand{\tr}{\text{tr}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}


\input{hui.tex}

\title{Calc III Sections
\\ 
\vspace{0.4cm}
\large Fall 2025}




\date{\today}
\author{Hui Sun}


\begin{document}

\maketitle

% \tableofcontents
\newpage


\begin{center}
    \Large Calc III-Week 1 (8/25-29)
\end{center}

\renewcommand\thesection{\arabic{section}}

\section{Logistics}


\begin{itemize}
    \item TA: Hui.
    \item Email: hsun95@jh.edu.
    \item Office Hour (tentative): Tuesday 4-6 PM, Krieger 211.
    \item Biweekly Quizzes: 10-15 min, 10\%.
    \item Attendance: 5\%. (If you can't make it, email me).
\end{itemize}

\section{Icebreaking Activity}

\begin{itemize}
    \item In a group of three or four: 
    \begin{enumerate}
        \item Learn each other names, year, pronouns.
        \item Find something in common and different among you and share with the entire class.
        \item Play Buzz if you have time, with prime $7$: say the number if it doens't contain or is not divisible by $7$, say buzz otherwise.
    \end{enumerate}
\end{itemize}


\section{Some Math}
\begin{prob}
    Draw the following vectors in $\R^2$:
    \begin{equation*}
        u=(1,2), \quad v=(3,-2)
    \end{equation*}
    Compute $u+v, u-v$, and draw them in the plane.
\end{prob}

\begin{prob}
    Consider the following vectors in $\R^3$:
    \begin{equation*}
        u=(1,2,3), \quad, v=(-2, 1, 4)
    \end{equation*}
    \begin{enumerate}
        \item Compute their norms.
        \item  Two vectors $a,b\in\R^3$ are called \textbf{orthognal} if $a\cdot b=0$. Are $u,v$ orthogonal? If not, find a nonzero vector orthogonal to $u$.
    \end{enumerate}
\end{prob}
$1+4+9=14$, $4+16+1=21$, 


\begin{prob}
    Let $u,v\in\R^3$, suppose that $u,v$ are orthongal, show that 
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2
    \end{equation*}
    Bonus: is the converse true?
\end{prob}
\begin{proof}
    
\end{proof}



\section{Reminders}
\begin{enumerate}
    \item First HW due this Friday.
    \item First Quiz next Tuesday.
\end{enumerate}
















\end{document}