\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\renewcommand{\familydefault}{ppl}
\newcommand{\tr}{\text{tr}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}


\input{hui.tex}

\title{Calc III Section Notes with Answers
\\ 
\vspace{0.4cm}
\large Fall 2025}




\date{\today}
\author{Hui Sun}


\begin{document}

\maketitle

% \tableofcontents
\newpage


\begin{center}
    \Large Calc III-Week 1 (8/25-29)
\end{center}

\renewcommand\thesection{\arabic{section}}

\textbf{Logistics}


\begin{itemize}
    \item TA: Hui.
    \item Email: hsun95@jh.edu.
    \item Office Hours: Tuesday 4-6 PM, Krieger 211; Friday 1-2 PM Zoom.
    \item Biweekly Quizzes: 15 min, 10\%.
    \item Attendance: 5\%. (If you can't make it, email me).
\end{itemize}

\textbf{Icebreaking Activity}

\begin{itemize}
    \item In a group of three or four: 
    \begin{enumerate}
        \item Learn each other names, year, pronouns.
        \item Find something in common and different among you and share with the entire class.
        \item Play Buzz if you have time, with prime $7$: say the number if it doens't contain or is not divisible by $7$, say buzz otherwise.
    \end{enumerate}
\end{itemize}


\textbf{Some Math}
\begin{prob}
    Draw the following vectors in $\R^2$:
    \begin{equation*}
        u=(1,2), \quad v=(3,-2)
    \end{equation*}
    Compute $u+v, u-v$, and draw them in the plane.
\end{prob}
\begin{proof}
    \begin{equation*}
        u+v=(4,0), \quad u-v=(-2, 4)
    \end{equation*}
\end{proof}

\begin{prob}
    Consider the following vectors in $\R^3$:
    \begin{equation*}
        u=(1,2,3), \quad, v=(-2, 1, 4)
    \end{equation*}
    \begin{enumerate}
        \item Compute their norms.
        \item  Two vectors $a,b\in\R^3$ are called \textbf{orthognal} if $a\cdot b=0$. Are $u,v$ orthogonal? If not, find a nonzero vector orthogonal to $u$.
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item \begin{equation*}
            \|u\|=(u\cdot u)^\frac{1}{2}=\sqrt{14}, \quad \|v\|=\sqrt{21}
        \end{equation*}
        \item We check 
        \begin{equation*}
            u\cdot v=-2+2+12=12\neq 0
        \end{equation*}
        thus not orthogonal. A vector that is orthognal to $u$: $(-3,0,1)$. Note that this vector is \textbf{not} unique! For example, $(-1,-1,1)$ is another such vector.
    \end{enumerate}
\end{proof}





\begin{prob}
    Let $u,v\in\R^3$, suppose that $u,v$ are orthongal, show that 
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2
    \end{equation*}
    Bonus: is the converse true? (meaning assuming $ \|u+v\|^2=\|u\|^2+\|v\|^2$, is it true that $u\cdot v=0$?)
\end{prob}
\begin{proof}
    We have 
    \begin{align*}
        \|u+v\|^2&=(u+v)\cdot(u+v)\\
        &=u\cdot u+u\cdot v+v\cdot u+v\cdot v\\
        &=\|u\|^2+\|v\|^2
    \end{align*}
    because $u\cdot v=v\cdot u=0$. The converse is also true: we know by definition that
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2+2u\cdot v
    \end{equation*}
    given the assumption, we also have 
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2
    \end{equation*}
    Thus equating them we get 
    \begin{equation*}
        \|u\|^2+\|v\|^2+2u\cdot v=\|u\|^2+\|v\|^2\Rightarrow u\cdot v=0
    \end{equation*}
\end{proof}



\textbf{Reminders}
\begin{enumerate}
    \item First HW due this Friday.
    \item First Quiz next Tuesday.
\end{enumerate}





\newpage



\begin{center}
    \Large Calc III-Week 2 (9/1-5)
\end{center}



\renewcommand\thesection{\arabic{section}}


\begin{defn}[cross product]
    Let $a=(a_1,a_2,a_3), b=(b_1,b_2,b_3)$ be vectors in $\R^3$, the cross product of $a,b$ is the vector $a\times b$, 
    \begin{equation*}
        a\times b=\begin{bmatrix}
            i&j&k\\
            a_1&a_2&a_3\\
            b_1&b_2&b_3
        \end{bmatrix}
    \end{equation*}
    where $i,j,k$ are the standard vectors in $\R^3$.
\end{defn}

\begin{defn}[Plane in three dimensions]
    A perpendicular vector and a normal vector uniquely define a plane in $\R^3$: given the plane $\mathcal{P}$ passing containing the point $(x_0,y_0,z_0)$ that has a normal vector $(A,B,C)$ is given by the equation:
    \begin{equation*}
        \mathcal{P}: A(x-x_0)+B(y-y_0)+C(z-z_0)=0
    \end{equation*}
\end{defn}

\begin{prop}
    Here are some properties of the cross product:
    \begin{enumerate}
        \item $a\times b$ is perpendicular to vectors $a,b$.
        \item The length of the cross product is the area of the parallelogram:
        \begin{equation*}
            \|a\times b\|=\|a\|\|b\|\sin\theta
        \end{equation*}
        where $\theta$ is the angle between them. (Compare this with the dot product).
        \item $a\times b=-b\times a$, and $a\times (b+c)=a\times b+a\times c$. Moreover, $a\times b=0$ iff $a,b$ are parallel or either $a$ or $b$ are $0$.
        \item (HW) The cross product is \textbf{not} associative! For example, compute 
        \begin{equation*}
            (i\times i)\times j, \quad i\times (i\times j)
        \end{equation*}
    \end{enumerate}
\end{prop}




\begin{prob}
    Let $\vec{u}=(1,2,3), \vec{v}=(0,1,1)$ be vectors in $\R^3$, compute the area of the parallelogram spanned by these two vectors.
\end{prob}
\begin{proof}
    \begin{equation*}
        u\times v=\begin{bmatrix}
            i&j&k\\
            1&2&3\\
            0&1&1
        \end{bmatrix}=-i-j+k=(-1,-1,1)
    \end{equation*}
    Thus the area of the parallelogram is 
    \begin{equation*}
        \|u\times v\|=\sqrt{3}
    \end{equation*}
\end{proof}

\begin{prob}
    Compute the plane containg all three points:
    \begin{equation*}
        (1,0,2), \quad (2, -1, 0), \quad (-1, 2, 3)
    \end{equation*}
\end{prob}
\begin{proof}
    Let $A=(1,0,2), B=(2, -1, 0), C=(-1, 2, 3)$, then consider two vectors in this plane 
    \begin{equation*}
        AB=(1,-1,-2), AC=(-2,2,1)
    \end{equation*}
    Then taking their cross product we find a normal vector to this plane:
    \begin{equation*}
        AB\times AC=\begin{bmatrix}
            i&j&k\\
            1&-1&-2\\
            -2&2&1
        \end{bmatrix}=3i+3j+0k=(3,3,0)
    \end{equation*}
    Thus using the definition above, and point $A$, we know the formula is given by 
    \begin{equation*}
        3(x-1)+3(y)=0
    \end{equation*}
    One can simplify this to 
    \begin{equation*}
        x+y-1=0
    \end{equation*}
\end{proof}


\textbf{Reminders}

HW is due Sunday 11:59PM.

% \begin{proof}
%     Find the cross product of $AB=(1,-1,-2), AC=(-2,2,1)$, the 
% \end{proof}


\newpage



\begin{center}
    \Large Calc III-Week 3 (9/8-9/12)
\end{center}

\renewcommand\thesection{\arabic{section}}

\noindent
Topics: (1) Graphing multivariable functions, (2) Introducing limits and continuity.

\begin{defn}[graph]
    The \textbf{image} of a function $f: \R^n\to\R^m$ is a subset of $\R^m$,
    \begin{equation*}
        \text{Image}(f)=\{f(x)\in\R^m: x\in\R^n\}
    \end{equation*}
    and the \textbf{graph} of $f$ is a subset of $\R^{n+m}$,
    \begin{equation*}
        \text{Graph}(f)=\{(x,f(x)): x\in\R^n\}
    \end{equation*}
\end{defn}



\begin{defn}[limit]
    Let $f: A\subset\R^n\to\R^m$, ($A$ is open), let $N$ be a neighborhood of a point $b\in\R^m$. Now let $x$ approach $x_0$ ($x_0\in\bar{A}$,) $f$ is said to be \textbf{eventually in $N$} if there exists a neighborhood $U$ of $x_0$ such that whenever $x\in U$, then $f(x)\in N$ as well. 

    The \textbf{limit} of $f$ as $x\to x_0$, if it exists, is $\lim_{x\to x_0}f(x):=b\in\R^m$ such that $f$ is eventually in $N$, for every neighborhood $N$ of $b$. 
\end{defn}

\begin{defn}[limit']
    $\lim_{x\to x'}f(x)=b$ is when $x=(x_1, x_2, \dots, x_n)\to x'=(x_1',x_2',\dots, x_n')$ from \textbf{all directions}, $f(x)$ approaches $b=(b_1,\dots, b_m)$.
\end{defn}



\begin{defn}[continuity]
    Let $f:A\subset\R^n\to\R^m$ is said to be \textbf{continuous} at $x_0\in A$ if 
    \begin{equation*}
        \lim_{x\to x_0}f(x)=f(x_0)
    \end{equation*}
    And $f$ is called continuous if $f$ is continuous at every $x_0\in A$.
\end{defn}

\begin{example}
    The limit doesn't need to exist! For example, let 
    \begin{equation*}
        H(x)=\begin{cases}
            1, x\geq 0\\
            -1, x<0
        \end{cases}
    \end{equation*}
    Note the limit doesn't exist at $x=0$.
\end{example}




\begin{prob}
    For the following functions, find their (1) image, (2) graph, (3) draw their graphs.
    \begin{enumerate}
        \item  Let $f: \R\to\R$, and $f(x)=x^2+1$.
        \item Let $g: \R^2\to \R$, and $g(x)=x^2+y^2$.
    \end{enumerate}
\end{prob}


\begin{prob}
    Compute the following limits:
    \begin{enumerate}
        \item \begin{equation*}
            \lim_{(x,y)\to (0,0)}\frac{\sin xy}{y}
        \end{equation*}
       ( Hint: try writing $\frac{\sin xy}{y}=\frac{\sin xy}{xy}\cdot x$, and recall $\lim_{t\to 0}\frac{\sin t}{t}=1$).
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{e^{xy}-1}{y}
        \end{equation*}
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{(x-y)^2}{x^2+y^2}
        \end{equation*}
    \end{enumerate}
\end{prob}
% \begin{proof}
%     \begin{enumerate}
%         \item Following the hint, we see 
%         \begin{equation*}
%             \lim_{(x,y)\to(0,0)}\frac{\sin xy}{y}=\lim_{(x,y)\to(0,0)}\frac{\sin xy}{xy}x=\lim_{x\to 0}x=0
%         \end{equation*}
%         \item This one uses the exact same trick: \begin{equation*}
%             \lim_{(x,y)\to(0,0)}\frac{e^{xy}-1}{xy}\cdot y=0
%         \end{equation*}
%         \item First letting $x\to 0$ along $y=0$, we see the limit is $1$; letting $x=y\to 0$, we see the limit is $0$, thus the limit doesn't exist!
%     \end{enumerate}
% \end{proof}


\begin{prob}
    Compute the limit of the following functions:
    \begin{enumerate}
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{x}{x+y} 
        \end{equation*}
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{xy}{x+y}
        \end{equation*}
        (Hint: try considering $y=x^2-x$ and $y=x$)
        \item \begin{equation*}
            \lim_{(x,y)\to (0,0)}\frac{\sin(xy)}{x+y}
        \end{equation*}
        % \item $f(x,y)=\frac{x}{x+y}$ as $(x,y)\to (0,0)$.
        % \item $g(x,y)=\frac{xy}{x+y}$ as $(x,y)\to (0,0)$.
        % \item $h(x,y)=\frac{\sin(xy)}{x+y}$ as $(x,y)\to (0,0)$. Recall that $\lim_{x\to 0}\frac{\sin(x)}{x}=1$.
    \end{enumerate}
\end{prob}
% \begin{proof}
%     \begin{enumerate}
%         \item First fix $x=0$, let $y\to 0$, then the limit is $0$; now fix $y=0$, let $x\to 0$, the limit is $1$. The limit doesn't exist!
%         \item Consider $y=x^2-x$, (as $x\to0, y\to 0$), then 
%         \begin{equation*}
%             \lim_{(x,y)\to(0,0)}\frac{xy}{x+y}=\lim_{x\to 0}\frac{x^3-x^2}{x^2}=\lim_{x\to 0}x-1=-1
%         \end{equation*}
%         and consider $y=x$, we see the limit is $0$, thus the limit doesn't exist!
%         \item We see that 
%         \begin{equation*}
%             \lim_{(x,y)\to(0,0)}\frac{\sin(xy)}{xy}\frac{xy}{x+y}
%         \end{equation*}
%         Note that the limit of $\sin(xy)/(xy)=1$, but the second one doesn't exist, thus the limit doesn't exist!
%     \end{enumerate}
% \end{proof}

\noindent
How to find a a limit $\lim_{x\to x_0}f(x)$:
\begin{itemize}
    \item Step 1: Guess what the limit should be.
    \item Step 2: Try from approaching $x_0$ from different directions.
    \item Step 3: Try to replace terms with expressions you are familiar with.
\end{itemize}














\end{document}