\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\renewcommand{\familydefault}{ppl}
\newcommand{\tr}{\text{tr}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}


\input{hui.tex}

\title{Functional Analysis
\\ 
\vspace{0.4cm}
\large Fall 2025}




\date{\today}
\author{Hui Sun}


\begin{document}

\maketitle

\chapter{Preliminary}

\section{9/3 lecture}



\begin{defn}[orthonormal basis]
    Let $S$ be an orthonormal set in the Hilbert space such that no other orthonormal set contains $S$ as a proper subset. Then $S$ is called an orthonormal basis.
\end{defn}

\begin{prop}
    Every Hilbert space admits an orthonormal basis.
\end{prop}
\begin{proof}
    Zorn's lemma.
\end{proof}
Remark: if $H$ is separable, i.e., $H$ has a countable dense subset, then the proof does not require Zorn's lemma. For example, $L^2$ is separable.

\begin{prop}[II.6, Parsevel's formula]
    Let $\mathcal{H}$ be a Hilbert space, and $S=\{x_n\}$ be an orthonormal basis, then for each $y\in\mathcal{H}$, 
    \begin{equation*}
        y=\sum_{\alpha\in\mathcal{A}}(x_\alpha,y)x_\alpha, \quad \|y\|^2=\sum|(x_n,y)|^2
    \end{equation*}
    where $\mathcal{A}$ is an index set.
\end{prop}
\begin{proof}
    Bessel's inequality states that for any $\mathcal{A}'\subset\mathcal{A}$ finite, we have 
    \begin{equation*}
        \sum_{\alpha\in\mathcal{A}'}|(x_\alpha,y)|^2\leq\|y\|^2<\infty
    \end{equation*}
    It follows that $|(x_\alpha,y)|>\frac{1}{n}$ for at most finitely many $\alpha$'s, and $|(x_\alpha,y)|\neq 0$ for at most countably many $\alpha$'s. Let $\{\alpha_i\}_{i=1}^\infty$ be an enumeration of such $\alpha$'s. Then 
    \begin{equation*}
        \sum_{i=1}^N|(x_{\alpha_i},y)|^2\leq\|y\|^2<\infty
    \end{equation*}
    which implies 
    \begin{equation*}
        \sum_{i=1}^\infty|(x_{\alpha_i},y)|^2<\infty
    \end{equation*}
    Let 
    \begin{equation*}
        y_n=\sum_{i=1}^n(x_{\alpha_i},y)x_{\alpha_i}, 
    \end{equation*}
    we would like to show that the sequence $\{y_n\}$ is cauchy, 
    \begin{equation*}
        \|y_n-y_m\|^2=\left\|\sum_{i=m+1}^n(x_{\alpha_i}, y)x_{\alpha_i}\right\|^2\to 0 \text{ as } m\to\infty
    \end{equation*}
    Thus $\{y_n\}$ is Cauchy. In other words,
    \begin{equation*}
        y_n\to y=\sum_{i=1}^\infty (x_{\alpha_i},y)x_{\alpha_i}
    \end{equation*}
\end{proof}


\begin{defn}
    A metric space is separable if it has a countable dense subset.
\end{defn}

\begin{prop}[II.7]
    Let $\mathcal{H}$ be a Hilbert space, then it is separable iff it has a countable orthonormal basis.
\end{prop}
\begin{proof}
    Suppose $\mathcal{H}$ is separable, let $\{x_n\}$ be a countable dense set, then we throw out terms in $\{x_n\}$ until we get a linearly indepedent dense subset $\{u_n\}\subset \{x_n\}$. Applying Gram-Schmidt, we can assume $\{u_n\}$ to be countable and orthonormal. Conversely, if $\{u_n\}$ is a countable orthonormal basis, then the set of linear combinations of $\{u_n\}$ with rational coefficients forms a countable dense subset of $\mathcal{H}$.
\end{proof}



\begin{defn}[Fourier Coefficient]
    The $n$th Fourier coefficient of a $2\pi$-periodic function $f$ is 
    \begin{equation*}
        c_n=\frac{1}{\sqrt{2\pi}}\int_0^{2\pi}e^{-inx}f(x)dx
    \end{equation*}
    The Fourier series of $f$ is 
    \begin{equation*}
        \tilde{f}(x)=\lim_{M\to\infty}
        \sum_{M=-N}^N\frac{1}{\sqrt{2\pi}}c_ne^{inx}
    \end{equation*}
\end{defn}

\begin{prop}
    The Fourier series $\sum_{k}c_k$ converges if $f\in L^2$. Moreover, the series converges uniformly to a continuous function if $\sum|c_k|<\infty$ 
\end{prop}
I am too lazzy to type it up, but it uses the fun lemma below:
\begin{lem}
    Suppose $f$ is $2\pi$-periodic, and $(f, e^{inx})=0$ for all $n$, then $f\equiv 0$. (In other words, if all the Fourier coefficients are $0$, then the function must be identically zero).
\end{lem}


\section{9/8 Lecture}
\begin{defn}[Banach space]
    A complete normed linear space is called a Banach space.
\end{defn}
\begin{example}
    \begin{enumerate}
        \item $L^\infty(\R)=\{f:f(x)\leq M \text{ a.e. }\}$, where $\|f\|_\infty$ is the smallest such $M$, is a Banach space.
        \item Let $C(\R)$ be the bounded continuous functions on $\R$. Let $C(\R)\subset L^\infty(\R)$ and equip it with the same norm. Moreover, $C(\R)$ is also a Banach space (due to the uniform convergence of continuous functions is still continuous).
        \item Let $C_c(\R)$ be the space of continuous functions with compact support, and this is not a Banach space under $\|\cdot\|_\infty$.
        \item $L^p$ is complete for all $1\leq p<\infty$.
        \item Let $a=\{a_n\}$ be a sequence of complex numbers, ad 
        \begin{equation*}
            \|a\|=\sup_n|a_n|<\infty
        \end{equation*}
        let $c_0=\{\lim_{n\to\infty}a_n=0\}$, $s=\{\lim_{n\to\infty}n^Na_n=0 \forall N\}$, and $l_p=\{\|a\|_p^p=\sum_{n=1}^\infty|a_n|^p<\infty\}$. Note that the space 
        \begin{equation*}
            f=\{a_n=0 \text{ for al but finitely many $n$}\}
        \end{equation*}
        is not complete! However, it is a dense subset in $l^p$. Morever, the set of elements in $f$ with rational coefficients, and the closure of $f$ in $s, l^p, c_0$ are exactly the whole spaces, i.e., $s,l^p, c_0$ are separable.
        \item Let $L(X,Y)$ be bounded linear operators from $X,Y$, with the operator norm, and $L(X,Y)$ is a Banach psace.
    \end{enumerate}
\end{example}

\begin{prop}
    Let $L^p(\R)$, where $1\leq p<\infty$ be the space of functions with the norm 
    \begin{equation*}
        \|f\|_p=\left(\int_\R|f(x)|^pdx\right)^p
    \end{equation*}
    then 
    \begin{enumerate}
        \item (Minkowski's inequality) $\|f\|_p\leq\|f\|_p+\|g\|_p$.
        \item (Riesz-Fischer) $L^p$ is complete.
        \item (Holder) Given $\frac{1}{p}+\frac{1}{q}=\frac{1}{r}$, we have 
        \begin{equation*}
            \|fg\|_r\leq\|f\|_p\|g\|_q
        \end{equation*}
        if $f\in L^p, g\in L^q$.
    \end{enumerate}
\end{prop}


\begin{prop}
    If $Y$ is complete, then $L(X,Y)$ is a Banach space.
\end{prop}
\begin{proof}
    Suppose $\{A_n\}$ is Cauchy, now we construct the limit: for each $x$, $A_nx=y_n$ is a Cauchy sequence:
    \begin{equation*}
        \|y_n-y_m\|\leq\|A_n-Am\|\cdot\|x\|
    \end{equation*}
    Now since $Y$ is complete, we know that $A_nx\to y$. Let $Ax=y$. (This is our limit)! Now $\|A_n\|\leq C$ for all $n$, which implies $\|A\|\leq C$. Thus $L(X,Y)$ is complete!
\end{proof}

\subsection{Duals}
\begin{defn}[dual space]
    The space of bounded linear functionals $L(X,\C)$, where $X$ is Banach, is called the dual space to $X$, denoted by $X^*$. Let $f\in X^*$, then define the norm 
    \begin{equation*}
        \|f\|=\sup_{x\in X, \|x\|\leq 1}|f(x)|
    \end{equation*}
\end{defn}


\begin{example}
    \begin{enumerate}
        \item Suppose that $1<p<\infty$, $\frac{1}{p}+\frac{1}{q}=1$, and let $g\in L^q$, then 
        \begin{equation*}
            G(f)=\int_{-\infty}^\infty\bar{g}(x)f(x)dx
        \end{equation*}
        Then $G$ is in $(L^p)^*$. Moreover, any such linear functional on $L^p$ can be written in this way for some $g\in L^q$. And 
        \begin{equation*}
            |G(f)|\leq\|f\|_p\|g\|_q
        \end{equation*}
        by Holder. Moreover, 
        \begin{equation*}
            L^q(\R)^*=L^p, (L^q(\R)^*)^*=L^q
        \end{equation*}
        because $L^q$ is reflexive! In particular, $L^2$ is its own dual space.
        \item Suppose $\{\lambda_k\}\subset l^q$, then 
        \begin{equation*}
            \Lambda(\{a_k\})=\sum_k\lambda_ka_k
        \end{equation*}
        is a bounded linear functional on $l^p$. Thus 
        \begin{equation*}
            l_q\subset (l^p)^*
        \end{equation*}
    \end{enumerate}
    for $1\leq p\leq\infty$. It turns out every linear functional on $l^p$ can be written in this form.
\end{example}
\begin{example}
    Let $p=1$, we have 
    \begin{equation*}
        L^1(\R)^*=L^\infty, \text{ but } L^\infty(\R)^*\neq L^1(\R)
    \end{equation*}
    in fact $L^\infty(\R)^*$ is bigger. 
\end{example}









\end{document}