\documentclass[openany]{book}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amsthm, amssymb}
\usepackage{yhmath}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{tikz-cd}
\usepackage{quiver}
\usepackage{hyperref,cleveref}
\renewcommand{\familydefault}{ppl}
\newcommand{\tr}{\text{tr}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\colim}{\text{colim}}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\disc}{disc}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\tor}{\text{Tor}}
\newcommand{\id}{\text{id}}
\newcommand{\ext}{\text{Ext}}
\newcommand{\ptop}{\text{PTop}}
\newcommand{\pt}{\text{pt}}
\newcommand{\ach}{\text{Ach}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\gal}{\text{Gal}}
\newcommand{\fraccomma}{\genfrac{}{}{0pt}{}{}{,}}
\newcommand{\diverg}{\operatorname{div}}
\newcommand{\curl}{\operatorname{curl}}
\definecolor{wikipediadarkblue}{rgb}{0.023, 0.270, 0.676}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=wikipediadarkblue,
    urlcolor=red
}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}


\input{hui_r.tex}

\title{Calc III Section Notes with Answers
\\ 
\vspace{0.4cm}
\large Spring 2026}




\date{\today}
\author{Hui Sun\\
(hsun95@jh.edu)}


\begin{document}

\maketitle
\tableofcontents

% \tableofcontents
\newpage

\chapter{The Geometry of Euclidean Spaces}


\section*{\centering Week 1 (1/19-23)}


% \begin{center}
%     \Large Calc III-Week 1 )
% \end{center}

\renewcommand\thesection{\arabic{section}}
\noindent
\textbf{Logistics}


\begin{itemize}
    \item TA: Hui.
    \item Email: hsun95@jh.edu.
    \item Drop-in Hours: Tuesday 2-3 PM, 4-5 pm, Krieger 211.
    \item Biweekly Quizzes: 10\%.
    \item Attendance: 5\%. (If you can't make it, email me).
\end{itemize}


\begin{defn}[standard basis of $\R^3$]
    The following vectors 
    \begin{equation*}
        i=(1,0,0), j=(0,1,0), k=(0,0,1)
    \end{equation*}
    are called the \textbf{standard basis} vectors of $\R^3$, and for any vector $a=(a_1,a_2,a_3)\in\R^3$, we can write 
    \begin{equation*}
        a=a_1i+a_2j+a_3k
    \end{equation*}
\end{defn}



\begin{defn}[dot product]
    Let $v=(v_1,v_2,v_3), w=(w_1,w_2, w_3)\in\R^3$, the \textbf{dot product} $v\cdot w$ is given by 
    \begin{equation*}
        v\cdot w=v_1w_1+v_2w_2+v_3w_3
    \end{equation*}
    Alternatively,
    \begin{equation*}
        v\cdot w=\|v\|\|w\|\cos\theta
    \end{equation*}
    where 
    \begin{equation*}
        \theta=\arccos\left(\frac{v\cdot w}{\|v\|\|w\|}\right)
    \end{equation*}
\end{defn}

\begin{defn}[length of vector]
    Let $v=(v_1,v_2,v_3)\in\R^3$, the \textbf{length} or \textbf{norm} of $v$, denoted as $\|v\|$, is 
    \begin{equation*}
        \|v\|=\sqrt{v_1^2+v_2^2+v_3^2}=\sqrt{v\dot v}
    \end{equation*}
\end{defn}

\begin{defn}[linear combination]
    Let $v, w\in\R^3$, a \textbf{linear combination} of $v,w$ is a sum 
    \begin{equation*}
        av+bw
    \end{equation*}
    for some $a,b\in\R$. One can generalize this definition to $n$ vectors: let $v_1, v_2\dots, v_n\in\R^3$, a linear combination of these vectors is a finite sum 
    \begin{equation*}
        a_1v_1+a_2v_2+\dots+a_nv_n
    \end{equation*}
    for some $a_i\in\R, 1\leq i\leq n$. 
\end{defn}


\begin{prop}[properties of the dot product]
    Let $a,b,c\in\R^n$, then 
    \begin{enumerate}
        \item[(a)] Nonnegativity: $a\cdot a\geq 0$, and $a\cdot a=0$ if and only if $a=0$.
        \item[(b)] Scalar multiplication: let $\lambda\in\R$, then 
        \begin{equation*}
            \lambda(a\cdot b)=\lambda a\cdot b=a\cdot \lambda b
        \end{equation*}
        \item[(c)] Distributivity:
        \begin{equation*}
            a\cdot(b+c)=a\cdot b+a\cdot c, \quad (a+b)\cdot c=a\cdot c+b\cdot c
        \end{equation*}
        \item[(d)] Symmetry: $a\cdot b=b\cdot a$.
    \end{enumerate}
\end{prop}


% \noindent
% \textbf{Icebreaking Activity}
% \begin{itemize}
%     \item In a group of three or four: 
%     \begin{enumerate}
%         \item Learn each other names, year, pronouns.
%         \item Find something in common and different among you and share with the entire class.
%         \item Play Buzz if you have time, with prime $7$: say the number if it doens't contain or is not divisible by $7$, say buzz otherwise.
%     \end{enumerate}
% \end{itemize}


\begin{prob}
    Draw the following vectors in $\R^2$:
    \begin{equation*}
        u=(1,2), \quad v=(3,-2)
    \end{equation*}
    Compute $u+v, u-v$, and draw them in the plane.
\end{prob}
\begin{proof}
    \begin{equation*}
        u+v=(4,0), \quad u-v=(-2, 4)
    \end{equation*}
\end{proof}

\begin{prob}
    Consider the following vectors in $\R^3$:
    \begin{equation*}
        u=(1,2,3), \quad, v=(-2, 1, 4)
    \end{equation*}
    \begin{enumerate}
        \item Compute their norms.
        \item  Two vectors $a,b\in\R^3$ are called \textbf{orthognal} if $a\cdot b=0$. Are $u,v$ orthogonal? If not, find a nonzero vector orthogonal to $u$.
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item \begin{equation*}
            \|u\|=(u\cdot u)^\frac{1}{2}=\sqrt{14}, \quad \|v\|=\sqrt{21}
        \end{equation*}
        \item We check 
        \begin{equation*}
            u\cdot v=-2+2+12=12\neq 0
        \end{equation*}
        thus not orthogonal. A vector that is orthognal to $u$: $(-3,0,1)$. Note that this vector is \textbf{not} unique! For example, $(-1,-1,1)$ is another such vector.
    \end{enumerate}
\end{proof}


\begin{prob}
    Can you express $w=(1,2)$ as a linear combination of $v_1,v_2$ for difference choices of $v_1,v_2$?
    \begin{enumerate}
        \item $v_1=(1,1), v_2=(-2,-2)$.
        \item $v_1=(2,1), v_2=(-1, 0)$.
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item We first note that $(1,1), (-2,-2)$ lie on the same line through the origin. Hence, any linear combination of $v_1,v_2$ will stay in this line, i.e., of the form $(a,a)$, for some $a\in\R$. Therefore, it is impossible to write $w=(1,2)$ as a linear combination of $v_1,v_2$.
        \item Suppose $w=a_1v_1+a_2v_2$ for some $a_1,a_2\in\R$, then 
        \begin{equation*}
            \begin{cases}
                2a_1-a_2=1\\
                a_1=2
            \end{cases}\Rightarrow \begin{cases}
                a_1=2\\
                a_2=3
            \end{cases}
        \end{equation*}
        Thus we can write $w$ as a linear combination of $v_1,v_2$:
        \begin{equation*}
            w=2v_1+3v_2
        \end{equation*}
    \end{enumerate}
\end{proof}





\begin{prob}
    Let $u,v\in\R^3$, suppose that $u,v$ are orthongal, show that 
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2
    \end{equation*}
    Bonus: is the converse true? (meaning assuming $ \|u+v\|^2=\|u\|^2+\|v\|^2$, is it true that $u\cdot v=0$?)
\end{prob}
\begin{proof}
    We have 
    \begin{align*}
        \|u+v\|^2&=(u+v)\cdot(u+v)\\
        &=u\cdot u+u\cdot v+v\cdot u+v\cdot v\\
        &=\|u\|^2+\|v\|^2
    \end{align*}
    because $u\cdot v=v\cdot u=0$. The converse is also true: we know by definition that
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2+2u\cdot v
    \end{equation*}
    given the assumption, we also have 
    \begin{equation*}
        \|u+v\|^2=\|u\|^2+\|v\|^2
    \end{equation*}
    Thus equating them we get 
    \begin{equation*}
        \|u\|^2+\|v\|^2+2u\cdot v=\|u\|^2+\|v\|^2\Rightarrow u\cdot v=0
    \end{equation*}
\end{proof}




\newpage

\section*{\centering Week 2 (1/26-30)}
Topics: determinant, cross product.

\begin{defn}[determinant]
    Let $A=\begin{pmatrix}
        a&b\\
        c&d
    \end{pmatrix}$ be a $2\times 2$ matrix, the \textbf{determinant} of $A$ is given by 
    \begin{equation*}
        \det(A)=ad-bc
    \end{equation*}
    Let $A=\begin{pmatrix}
        a_1&a_2&a_3\\
        b_1&b_2&b_3\\
        c_1&c_2&c_3
    \end{pmatrix}$ be a $3\times 3$ matrix, the \textbf{determinant} of $A$ is given by
    \begin{equation*}
        \det(A)=a_1(b_2c_3-b_3c_2)-a_2(b_1c_3-b_3c_1)+a_3(b_1c_2-b_2c_1)
    \end{equation*}
\end{defn}


\begin{defn}[cross product]
    Let $a,b\in\R^3$, write $a=(a_1,a_2,a_3), b=(b_1,b_2,b_3)$, then the \textbf{cross product}
    \begin{equation*}
        a\times b=\det\begin{bmatrix}
            i&j&k\\
            a_1&a_2&a_3\\
            b_1&b_2&b_3
        \end{bmatrix}
    \end{equation*}
    where $i,j,k$ are the standard vectors in $\R^3$.
\end{defn}


\begin{prop}[properties of the cross product]
    We have the following properties regarding the cross product: let $a,b\in\R^3$,
    \begin{enumerate}
        \item $a\times a=0$.
        \item $a\times b=-b\times a$.
        \item $(a+b)\times c=a\times c+b\times c$, and $a\times (b+c)=a\times b+a\times c$.
        \item $(\alpha a)\times b=\alpha(a\times b)$ for any $a\in\R$.
        \item $a\times b$ is perpendicular to vectors $a,b$.
        \item The length of the cross product is the area of the parallelogram spanned by $a,b$:
        \begin{equation*}
            \|a\times b\|=\|a\|\|b\|\sin\theta
        \end{equation*}
        where $0\leq\theta\leq\pi$ is the angle between them. 
        \item $a\times b=0$ iff $a,b$ are parallel or either $a$ or $b$ are $0$.
        \item The cross product is \textbf{not} associative! For example, compute 
        \begin{equation*}
            (i\times i)\times j, \quad i\times (i\times j)
        \end{equation*}
    \end{enumerate}
\end{prop}


\begin{prop}[determinant and linear combination]\label{det}
    Let $A=\begin{pmatrix}
        a_1&a_2&a_3\\
        b_1&b_2&b_3\\
        c_1&c_2&c_3
    \end{pmatrix}$ be a $3\times 3$ matrix, let 
    \begin{equation*}
        a=(a_1,a_2, a_3), b=(b_1,b_2,b_3), c=(c_1,c_2,c_3)
    \end{equation*}
    If any of $a,b,$ or $c$ is a linear combination of the other two vectors, then $\det(A)=0$. (Relevant topic: linear independence).
\end{prop}



\begin{prob}
    Let $\vec{u}=(1,2,3), \vec{v}=(0,1,1)$ be vectors in $\R^3$, compute the area of the parallelogram spanned by these two vectors.
\end{prob}
\begin{proof}
    \begin{equation*}
        u\times v=\begin{bmatrix}
            i&j&k\\
            1&2&3\\
            0&1&1
        \end{bmatrix}=-i-j+k=(-1,-1,1)
    \end{equation*}
    Thus the area of the parallelogram is 
    \begin{equation*}
        \|u\times v\|=\sqrt{3}
    \end{equation*}
\end{proof}


\begin{prob}
    Compute the determinant of the following matrix $A$:
    \begin{equation*}
        A=\begin{pmatrix}
            1&0&2\\
            2&1&-1\\
            3&1&1
        \end{pmatrix}
    \end{equation*}
\end{prob}
\begin{proof}
    Notice that the third row vector $(3,1,1)$ is the sum of the two row vectors above, hence by Proposition \ref{det}, we know we must have $\det(A)=0$.
\end{proof}
\newpage

\section*{\centering Week 2 (Section Activity)}
First, introduce yourself to one another:
\begin{enumerate}
    \item Name.
    \item Pronouns.
    \item Year.
    \item Major.
    \item If you could have a noncat, nondog pet, what would it be?
\end{enumerate}
Next, work on and \textbf{discuss} the following problems!
\begin{prob}
    Let $u=(1,2,-1)$, find a nonzero vector that is orthogonal to $u$.
\end{prob}
\begin{proof}
    There are many choices, for example, $v=(1,0,1)$.
\end{proof}

\begin{prob}
    Let $u=(1,0), v=(2,-1)$, 
    \begin{enumerate}
        \item Using the dot product, what is the angle between $u,v$? (You do not need to simplify your answer).
        \item Can you find a nonzero vector in $\R^2$ that is orthogonal to both of $u,v$? 
        \item Can you find nonzero vectors that are orthogonal to any basis of $\R^2$? (Hint: take $u=(1,0)$, can you draw the set of vectors orthogonal to $u$? A basis of $\R^2$ contains two noncolinear vectors).
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item We have 
        \begin{equation*}
            \cos\theta=\frac{u\cdot v}{\|u\|\|v\|}=\frac{2}{\sqrt{5}}
        \end{equation*}
        Hence 
        \begin{equation*}
            \theta=\arccos\left(\frac{2}{\sqrt{5}}\right)
        \end{equation*}
        \item Suppose there exists a nonzero vector $w=(w_1,w_2)\in\R^2$ such that $w\cdot u=w\cdot v=0$, then this implies
        \begin{equation*}
            w\cdot u=w_1=0, \quad w\cdot v=2w_1-w_2=0\Rightarrow w_1=w_2=0
        \end{equation*}
        Thus the only vector orthogonal to $u,v$ is the zero vector, hence the answer is no.
        \item Let $\{a,b\}$ be a basis of $\R^2$, where $a=(a_1,a_2), b=(b_1,b_2)$, we know they are noncolinear, hence 
        \begin{equation*}
            \frac{a_1}{b_1}\neq\frac{a_2}{b_2}
        \end{equation*}
        Then suppose $w$ is orthogonal to both $a,b$. Then (one can draw a picture), $w$ should be of the form 
        \begin{equation*}
            w=(\lambda a_2,-\lambda a_1)=(\zeta b_2, -\zeta b_1)
        \end{equation*}
        for some $\lambda,\zeta\in\R$. But this implies 
        \begin{equation*}
            \frac{a_1}{b_1}=\frac{a_2}{b_2}=\frac{\zeta}{\lambda}
        \end{equation*}
        which is a contradiction to the above. This concludes the proof that no nonzero vector can be orthogonal to a basis in $\R^2$.
    \end{enumerate}
\end{proof}

\begin{prob}
    Let 
    \begin{equation*}
        A=\begin{pmatrix}
            1&2&0\\
            -1&3&1\\
            0&0&2
        \end{pmatrix}
    \end{equation*}
    Compute the determinant of $A$.
\end{prob}
\begin{proof}
    We have $\det(A)=10$.
\end{proof}

\begin{prob}
    Construct a nonzero $3\times 3$ matrix $A$ such that $\det(A)=0$.
\end{prob}
\begin{proof}
    \begin{equation*}
        A=\begin{pmatrix}
            1&1&1\\
            2&2&2\\
            3&3&3
        \end{pmatrix}
    \end{equation*}
\end{proof}


\newpage 
\section*{\centering Week 3 (2/2-2/6)}
Topics: parametric equations, multivariable functions, and level sets.

\begin{defn}[matrix addition, multiplication]
    Let $A, B$ be $m\times n$ matrices, $C$ be $n\times k$ matrix as follows 
    \begin{equation*}
        A=\begin{pmatrix}
            a_{11}&\dots& a_{1n}\\
            \vdots&\ddots&\vdots\\
            a_{m1}&\dots&a_{mn}
        \end{pmatrix}, \quad B=\begin{pmatrix}
            b_{11}&\dots&b_{1n}\\
            \vdots&\ddots&\vdots\\
            b_{m1}&\dots&b_{mn}
        \end{pmatrix}
    \end{equation*}
    \begin{equation*}
        C=\begin{pmatrix}
            c_{11}&\dots&c_{1k}\\
            \vdots&\ddots&\vdots\\
            c_{n1}&\dots&c_{nk}
        \end{pmatrix}
    \end{equation*}
    then \textbf{matrix addition} $A+B$ defined as 
    \begin{equation*}
        A+B\coloneq\begin{pmatrix}
            a_{11}+b_{11}&\dots& a_{1n}+b_{1n}\\
            \vdots&\ddots&\vdots\\
            a_{m1}+b_{m1}&\dots&a_{mn}+b_{mn}
        \end{pmatrix}
    \end{equation*}
    and \textbf{matrix multiplication} is defined as 
    \begin{equation*}
        AC=\begin{pmatrix}
            \sum_{j=1}^na_{1j}c_{j1}&\dots&\sum_{j=1}^na_{1j}c_{jk}\\
            \vdots&\ddots&\vdots\\
            \sum_{j=1}^na_{mj}c_{j1}&\dots&\sum_{j=1}^na_{mj}c_{jk}
        \end{pmatrix}
    \end{equation*}
    \begin{remark}
        Given matrices $A,B$, for the matrix multiplication $AB$ to be well-defined,
        \begin{equation*}
            \text{number of columns of $A$}=\text{number of rows of $B$}
        \end{equation*}
    \end{remark}
\end{defn}

\begin{defn}[matrix as linear transformation]
    Let $A$ be an $m\times n$ matrix 
    \begin{equation*}
        A=\begin{pmatrix}
            a_{11}&\dots& a_{1n}\\
            \vdots&\ddots&\vdots\\
            a_{m1}&\dots&a_{mn}
        \end{pmatrix}
    \end{equation*}
    and let $x\in\R^n$, where $x=(x_1,\dots, x_n)$. Then $A$ applied to $x$ as a linear transformation is given by 
    \begin{equation*}
        Ax=\begin{pmatrix}
            a_{11}&\dots& a_{1n}\\
            \vdots&\ddots&\vdots\\
            a_{m1}&\dots&a_{mn}
        \end{pmatrix}\begin{pmatrix}
            x_1\\
            \vdots\\
            x_n
        \end{pmatrix}=\begin{pmatrix}
            \sum_{j=1}^na_{1j}x_j\\
            \vdots\\
            \sum_{j=1}^na_{mj}x_j
        \end{pmatrix}
    \end{equation*}
    where 
    \begin{equation*}
        \sum_{j=1}^na_{1j}x_j=a_{11}x_1+a_{12}x_2+\dots+a_{1n}x_n, \quad\dots
    \end{equation*}
\end{defn}


\begin{defn}[image, graph]
    The \textbf{image} of a function $f:U\subset \R^n\to\R^m$ is a subset of $\R^m$,
    \begin{equation*}
        \text{Image}(f)=\{f(x)\in\R^m: x\in U\}
    \end{equation*}
    and the \textbf{graph} of $f$ is a subset of $\R^{n+m}$,
    \begin{equation*}
        \text{Graph}(f)=\{(x,f(x)): x\in U\}
    \end{equation*}
\end{defn}


\begin{defn}[level set]
    Let $f:U\subset\R^n\to\R^m$, and $c\in\R$ be some constant. Then the \textbf{level set} of $f$ at $c$ is the set $\mathcal{L}_c$
    \begin{equation*}
        \mathcal{L}_c\coloneq\{x\in U: f(x)=c\}\subset\R^n
    \end{equation*}
\end{defn}

\begin{defn}[Equation of a line]\label{line}
    A \textbf{line} $l$ in $\R^3$ through the tip of $a=(a_1,a_2,a_3)$ pointing in the direction of a vector $v=(v_1,v_2,v_3)$ is given by 
    \begin{equation*}
        l(t)=a+tv=(a_1+tv_1, a_2+tv_2, a_3+tv_3)
    \end{equation*}
    where $t\in\R$. Alternatively, a line passing through two points $P=(x_1,y_1,z_1), Q=(x_2,y_2,z_2)$ is given by 
    \begin{equation*}
        l(t)=(x(t), y(t), z(t))
    \end{equation*}
    where 
    \begin{equation*}
        \begin{cases}
            x(t)=x_1+(x_2-x_1)t\\
            y(t)=y_1+(y_2-y_1)t\\
            z(t)=z_1+(z_2-z_1)t
        \end{cases}
    \end{equation*}
\end{defn}


\begin{defn}[Plane in $\R^3$]\label{plane}
    If a plane ${P}$ passes through some point $(x_0,y_0,z_0)$, and $n=(A,B,C)$ is a vector orthogonal to the plane, then the plane ${P}$ is given by the equation:
     \begin{equation*}
         A(x-x_0)+B(y-y_0)+C(z-z_0)=0
     \end{equation*}
     \begin{remark}
        A point ${P}$ in the plane and a normal vector to the plane uniquely determine a plane in $\R^3$. Equivalently, three noncolinear points uniquely determine a plane.
     \end{remark}
 \end{defn}
 \begin{prob}
    Compute the plane containing all three points:
    \begin{equation*}
        (1,0,2), \quad (2, -1, 0), \quad (-1, 2, 3)
    \end{equation*}
 \end{prob}
 \begin{proof}
    Let $A=(1,0,2), B=(2, -1, 0), C=(-1, 2, 3)$, then consider two vectors in this plane 
    \begin{equation*}
        AB=(1,-1,-2), AC=(-2,2,1)
    \end{equation*}
    Then taking their cross product we find a normal vector to this plane:
    \begin{equation*}
        AB\times AC=\begin{bmatrix}
            i&j&k\\
            1&-1&-2\\
            -2&2&1
        \end{bmatrix}=3i+3j+0k=(3,3,0)
    \end{equation*}
    Thus using the definition above, and point $A$, we know the formula is given by 
    \begin{equation*}
        3(x-1)+3(y)=0
    \end{equation*}
    One can simplify this to 
    \begin{equation*}
        x+y-1=0
    \end{equation*}
\end{proof}

 \begin{prob}
    \begin{enumerate}
        \item[(a)] Find the equation of the line through \( (1, 1, 0) \) in the direction of \( 2\mathbf{i} - \mathbf{k} \).  
        \item[(b)] Find the equation of the line passing through \( (0, 1, 1) \) and \( (0, 1, 0) \).  
        \item[(c)] Find an equation for the plane perpendicular to the vector \( (-1, 1, -1) \) and passing through the point \( (1, 1, 1) \).
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item[(a)] The equation is given by 
        \begin{equation*}
            l_1(t)=(1,1,0)+t(2, 0, -1), \quad t\in\R
        \end{equation*}
        \item[(b)] The equation is given by 
        \begin{equation*}
            l_2(t)=(0,1,1)+t(0, 0, -1), \quad t\in\R
        \end{equation*}
        \item[(c)] The equation of the plane is given by 
        \begin{equation*}
            (x-1, y-1, z-1)\cdot (-1, 1, -1)=0
        \end{equation*}
        simplifying we get 
        \begin{equation*}
            x-y+z=1
        \end{equation*}
    \end{enumerate}
\end{proof}


\chapter{Differentiation}

\section*{\centering Week 4 (2/9-2/13)}
Topic: limits.






\begin{defn}[limit]
    Let $f: A\subset\R^n\to\R^m$, where $A$ is open, let $x_0$ be in $A$ or be a boundary point of $A$ and $N$ be a neighborhood of a point $b\in\R^m$. Now let $x$ approach $x_0$, $f$ is said to be \textbf{eventually in $N$} if there exists a neighborhood $U$ of $x_0$ such that 
    \begin{equation*}
        \text{ if } x\in U, \text{ then } f(x)\in N
    \end{equation*}
    If $f$ is eventually in $N$ for \textit{any} neighborhood $N$ around $b$, then the \textbf{limit} of $f$ as $x\to x_0$ exists, denoted as 
    \begin{equation*}
        \lim_{x\to x_0}f(x)=b
    \end{equation*}
    Alternatively, if the limit exists, then $\lim_{x\to x'}f(x)=b$ is when $x=(x_1, x_2, \dots, x_n)\to x'=(x_1',x_2',\dots, x_n')$ from \textbf{all directions}, and $f(x)$ approaches $b=(b_1,\dots, b_m)$.
\end{defn}



\begin{defn}[continuity]
    Let $f:A\subset\R^n\to\R^m$ is said to be \textbf{continuous} at $x_0\in A$ if 
    \begin{equation*}
        \lim_{x\to x_0}f(x)=f(x_0)
    \end{equation*}
    And $f$ is called continuous if $f$ is continuous at every $x_0\in A$.
\end{defn}

\begin{example}
    The limit doesn't need to exist! For example, let 
    \begin{equation*}
        H(x)=\begin{cases}
            1, x\geq 0\\
            -1, x<0
        \end{cases}
    \end{equation*}
    Note the limit doesn't exist at $x=0$.
\end{example}




\begin{prob}
    For the following functions, find their (1) image, (2) graph, (3) \textbf{draw their level sets}.
    \begin{enumerate}
        \item  Let $f: \R\to\R$, and $f(x)=x^2+1$.
        \item Let $g: \R^2\to \R$, and $g(x,y)=x^2+y^2$.
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item $\text{Image}(f)=\{x^2+1: x\in\R\}$, and $\text{Graph}(f)=\{(x,x^2+1):x\in\R\}$.
        \item $\text{Image}(g)=\{x^2+y^2, (x,y)\in\R^2\}$, and $\text{Graph}(g)=\{(x,y,x^2+y^2):(x,y)\in\R^2\}$.
    \end{enumerate}
\end{proof}

\begin{prob}
    Compute the following limits:
    \begin{enumerate}
        \item \begin{equation*}
            \lim_{(x,y)\to (0,0)}\frac{\sin xy}{y}
        \end{equation*}
       ( Hint: try writing $\frac{\sin xy}{y}=\frac{\sin xy}{xy}\cdot x$, and recall $\lim_{t\to 0}\frac{\sin t}{t}=1$).
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{e^{xy}-1}{y}
        \end{equation*}
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{(x-y)^2}{x^2+y^2}
        \end{equation*}
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item Following the hint, we see 
        \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{\sin xy}{y}=\lim_{(x,y)\to(0,0)}\frac{\sin xy}{xy}x=\lim_{x\to 0}x=0
        \end{equation*}
        \item This one uses the exact same trick: \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{e^{xy}-1}{xy}\cdot y=0
        \end{equation*}
        \item First letting $x\to 0$ along $y=0$, we see the limit is $1$; letting $x=y\to 0$, we see the limit is $0$, thus the limit doesn't exist!
    \end{enumerate}
\end{proof}


\begin{prob}
    Compute the limit of the following functions:
    \begin{enumerate}
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{x}{x+y} 
        \end{equation*}
        \item \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{xy}{x+y}
        \end{equation*}
        (Hint: try considering $y=x^2-x$ and $y=x$)
        \item \begin{equation*}
            \lim_{(x,y)\to (0,0)}\frac{\sin(xy)}{x+y}
        \end{equation*}
        % \item $f(x,y)=\frac{x}{x+y}$ as $(x,y)\to (0,0)$.
        % \item $g(x,y)=\frac{xy}{x+y}$ as $(x,y)\to (0,0)$.
        % \item $h(x,y)=\frac{\sin(xy)}{x+y}$ as $(x,y)\to (0,0)$. Recall that $\lim_{x\to 0}\frac{\sin(x)}{x}=1$.
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item First fix $x=0$, let $y\to 0$, then the limit is $0$; now fix $y=0$, let $x\to 0$, the limit is $1$. The limit doesn't exist!
        \item Consider $y=x^2-x$, (as $x\to0, y\to 0$), then 
        \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{xy}{x+y}=\lim_{x\to 0}\frac{x^3-x^2}{x^2}=\lim_{x\to 0}x-1=-1
        \end{equation*}
        and consider $y=x$, we see the limit is $0$, thus the limit doesn't exist!
        \begin{warn}
            2 does not follow from 1! A student suggests a proof: $\lim_{(x,y)\to(0,0)}=\frac{x}{x+y}\cdot y$, and by 1, the limit $\frac{x}{x+y}$ doesn't exist, this implies the limit of $\frac{xy}{x+y}$ also doesn't exist. This argument is not correct! Consider the following counterexample: $\lim_{y\to 0}\frac{1}{y}$ doesn't exist, but the limit
            \begin{equation*}
                \lim_{y\to 0}\frac{1}{y}\cdot y=1
            \end{equation*}
            exists! More concretely, if you multiply by any function that doesn't tend to $0$, the argument follows, but it doesn't work when the function tends to $0$!
        \end{warn}
        \item We see that 
        \begin{equation*}
            \lim_{(x,y)\to(0,0)}\frac{\sin(xy)}{xy}\frac{xy}{x+y}
        \end{equation*}
        Note that the limit of $\sin(xy)/(xy)=1$, but the second one doesn't exist, thus the limit doesn't exist!
    \end{enumerate}
\end{proof}


\noindent
\begin{idea}
How to find a a limit $\lim_{x\to x_0}f(x)$:
\begin{itemize}
    \item Step 1: Guess what the limit should be.
    \item Step 2: Try from approaching $x_0$ from different directions.
    \item Step 3: Try to replace terms with expressions you are familiar with.
\end{itemize}
\end{idea}


\newpage 
\section*{\centering Week 5 (2/16-2/20)}
Topic: derivatives.

\begin{defn}[partial derivative]
    Let $f:U\subset\R^n\to\R$, where $U$ is open. Then the \textbf{partial derivative} with respect to $x_i$ is defined by 
    \begin{equation*}
        \frac{\partial f}{\partial x_i}(x_1, \dots, x_n)=\lim_{h\to 0}\frac{f(x+he_i)-f(x)}{h}
    \end{equation*}
    where $e_i=(0,\dots, 1,\dots, 0)$ with $1$ in the $i$th coordinate. 
\end{defn}




\begin{defn}[differentiability in two variables]
    Let $f:U\subset\R^2\to\R$, then $f$ is \textbf{differentiable} at $(x_0,y_0)\in U$ if 
    \begin{enumerate}
        \item[(1)] $\frac{\partial f}{\partial x},\frac{\partial f}{\partial y}$ exist at $(x_0,y_0)$
        \item[(2)] 
        \begin{equation*}
            \lim_{(x,y)\to(x_0,y_0)}\frac{f(x,y)-f(x_0,y_0)-\left[\frac{\partial f}{\partial x}(x_0,y_0)\right](x-x_0)-\left[\frac{\partial f}{\partial y}(x_0,y_0)\right](y-y_0)}{\|(x,y)-(x_0,y_0)\|}=0
        \end{equation*}
    \end{enumerate}
    If $f$ is differentiable at $(x_0, y_0)$, then the derivative of $f$ at $(x_0,y_0)$ is the $1\times 2$ matrix 
    \begin{equation*}
        \begin{bmatrix}\frac{\partial f}{\partial x}(x_0,y_0)&\frac{\partial f}{\partial y}(x_0,y_0)\end{bmatrix}
    \end{equation*}
\end{defn}
\begin{warn}
    It is not enough only require the partial derivatives exist at the point. Consider the following function:
    \begin{equation*}
        f(x,y)=\begin{cases}
            \frac{xy}{x^2+y^2}, & (x,y)\neq (0,0)\\
            0, & (x,y)=(0,0)
        \end{cases}
    \end{equation*}
    The partitial derivatives exist at $(0,0)$, but $f$ is not differentiable.
\end{warn}



\begin{defn}[tangent plane]
    Let $f:\R^2\to\R$ be differentiable at $(x_0,y_0)$, then the \textbf{tangent plane} to the graph $f$ at $(x_0, y_0)$ is the given by 
    \begin{equation*}
        z=f(x_0,y_0)+\frac{\partial f}{\partial x}(x_0,y_0)(x-x_0)+\frac{\partial f}{\partial y}(x_0,y_0)(y-y_0)
    \end{equation*}
    \begin{remark}
        The plane given above intersects the graph of $f$ at the point $(x_0, y_0, f(x_0, y_0))$.
    \end{remark}
\end{defn}


\begin{defn}[differentiability in the general setting]
    Let $f:U\subset\R^n\to\R^m$, then $f$ is differentiable at $x_0\in U$ if
    \begin{enumerate}
        \item[(1)] the partial derivatives $\frac{\partial f_i}{\partial x_j}$ exist for all $1\leq i\leq m, 1\leq j\leq n$. 
        \item[(2)]
        \begin{equation*}
            \lim_{x\to x_0}\frac{\|f(x)-f(x_0)-T(x-x_0)\|}{\|x-x_0\|}=0
        \end{equation*}
        where $T=Df(x_0)$ is the $m\times n$ matrix 
        \begin{equation*}
            Df(x_0)=
            \begin{bmatrix}
            \frac{\partial f_1}{\partial x_1}(x_0) & \cdots & \frac{\partial f_1}{\partial x_n}(x_0) \\
            \vdots & \ddots & \vdots \\
            \frac{\partial f_m}{\partial x_1}(x_0) & \cdots & \frac{\partial f_m}{\partial x_n}(x_0)
            \end{bmatrix}
        \end{equation*}
    \end{enumerate}
    % The derivative of $f$ at $x_0$ is the $m\times n$ matrix $Df(x_0)$.
    % \begin{remark}
    %     When $m=1$, the derivative becomes a $1\times n$ matrix, we call this the \textbf{gradient} of $f$.
    % \end{remark}
\end{defn}

\begin{defn}[gradient]
    Let $f:U\subset\R^n\to\R$, the \textbf{gradient} $\nabla f(x)$ is a special case of the general case above when $m=1$, i.e., it is a $1\times n$ matrix 
    \begin{equation*}
        Df(x)=\begin{bmatrix}
            \frac{\partial f}{\partial x_1}&\dots&\frac{\partial f}{\partial x_n}
        \end{bmatrix}
    \end{equation*}
\end{defn}



\begin{prop}
    Let $f:U\subset\R^n\to\R^m$ be differentiable at $x_0$, then the derivative of $f$ at $x_0$ is an $m\times n$ matrix $Df(x_0)=\left(\frac{\partial f_i}{\partial x_j}\right)_{ij}$. The derivative follows the same properties as derivative for single variable functions:
    \begin{enumerate}
        \item Let $c\in\R$, then 
        \begin{equation*}
            D(cf)(x_0)=cDf(x_0) \tag {multiplication of a matrix by constant $c$}
        \end{equation*}
        \item Let $g: U\subset\R^n\to\R^m$ also be differentiable at $x_0$, then 
        \begin{equation*}
            D(f+g)(x_0)=Df(x_0)+Dg(x_0) \tag{sum of two matrices}
        \end{equation*}
        \item Let $h_1: U\subset\R^n\to\R, h_2: U\subset\R^n\to\R$,then 
        \begin{equation*}
            D(h_1h_2)(x_0)=Dh_1(x_0)h_2(x_0)+h_1(x_0)Dh_2(x_0) \tag{product rule}
        \end{equation*}
        and if $h_2\neq 0$ on $U$.
        \begin{equation*}
            D(h_1/h_2)(x_0)=\frac{Dh_1(x_0)h_2(x_0)-h_1(x_0)Dh_2(x_0)}{h_2^2(x_0)} \tag{quotient rule}
        \end{equation*}
        \item Let $g: U\subset\R^n\to\R^m, f:V\subset\R^m\to\R^p$ such that $g(U)\subset V$, then 
        \begin{equation*}
            D(f\circ g)(x_0)=Df(g(x_0))Dg(x_0) \tag{chain rule}
        \end{equation*}
    \end{enumerate}
\end{prop}

\begin{prop}[special case of chain rule]
    Let $f:\R^3\to\R$ be a function in $3$ variables $u,v,w$, namely, $z=f(u,v,w)$, and if $u=g_1(x), v=g_2(x), w=g_3(x)$, then 
    \begin{equation*}
        \frac{\partial z}{\partial x}=\frac{\partial z}{\partial u}\frac{\partial u}{\partial x}+\frac{\partial z}{\partial v}\frac{\partial v}{\partial x}+\frac{\partial z}{\partial w}\frac{\partial w}{\partial x}
    \end{equation*}
\end{prop}

\newpage 
\begin{prob}
    Compute the plane tangent to the graph of $f(x,y)=x^2y+2xy-y^2$ at $(1,2,2)$.
\end{prob}
\begin{proof}
    We have 
    \begin{equation*}
        \frac{\partial f}{\partial x}(1,2)=2xy+2y\vert_{(1,2)}=8, \quad \frac{\partial f}{\partial y}(1,2)=x^2+2x-2y\vert_{(1,2)}=-1
    \end{equation*}
    and $f(1,2)=2$, thus the plane is given by
    \begin{equation*}
        z=2+8(x-1)-(y-2)
    \end{equation*}
    i.e., $z=8x-y-4$.
\end{proof}


% \begin{example}
%     Let $f(x,y,z)=(ze^x, -ye^z)$, then 
%     \[
% Df(x, y, z) = 
% \begin{bmatrix}
% ze^x & 0 & e^x \\
% 0 & -e^z & -ye^z
% \end{bmatrix}
% \]
% \end{example}



\begin{prob}
    Let \( f : \mathbb{R}^3 \to \mathbb{R} \) be defined by  
\[
f(x, y, z) = x^2 y + y \sin(z) + z e^x.
\]  
Compute the gradient of $f$ at $(1,2,0)$.
\end{prob}
\begin{proof}
    You can compute the partial derivatives 
    \begin{align*}
        \frac{\partial f}{\partial x} &= 2xy + ze^x, \\
        \frac{\partial f}{\partial y} &= x^2 + \sin(z), \\
        \frac{\partial f}{\partial z} &= y \cos(z) + e^x.
        \end{align*}
    thus the gradient is 
    \[
\nabla f = \left( \frac{\partial f}{\partial x}, \frac{\partial f}{\partial y}, \frac{\partial f}{\partial z} \right)=(2xy+ze^x, x^2+\sin z, y\cos z+e^x)
\]
Hence 
\begin{equation*}
    \nabla f(1,2,0)=(4, 1, 2+e)
\end{equation*}
\end{proof}


\begin{prob}
    Given $w=2xy+z$, where $x=2t, y=-t, z=t^2$, compute $\frac{\partial w}{\partial t}$.
\end{prob}
\begin{proof}
    Using chain rule, we write 
    \begin{equation*}
        \frac{\partial w}{\partial t}=\frac{\partial w}{\partial x}\frac{\partial x}{\partial t}+\frac{\partial y}{\partial t}\frac{\partial y}{\partial t}+\frac{\partial z}{\partial t}\frac{\partial z}{\partial t}=4y-2x+2t=-6t
    \end{equation*}

\end{proof}



\begin{prob}[2.5, Q7]
    Let \( f(u, v) = (\tan (u - 1) - e^v, u^2 - v^2) \) and  
   \[
   g(x, y) = (e^{x-y}, x - y).
   \]  
   Calculate \( f \circ g \) and  
   \[
   D(f \circ g)(1, 1).
   \]
\end{prob}
\begin{proof}
    We have 
    \begin{equation*}
        f\circ g(x,y)=(\tan(e^{x-y}-1)-e^{x-y}, e^{2(x-y)}-(x-y)^2)
    \end{equation*}
    and $g(1,1)=(1,0)$, thus using chain rule, we have 
    \begin{equation*}
        D(f\circ g)(1,1)=Df(1,0)Dg(1,1)
    \end{equation*}
    where 
    \begin{equation*}
        Df(u,v)=\begin{bmatrix}
            \sec^2(u-1)& -e^v\\
            2u&-2v
        \end{bmatrix}, \quad Dg(x,y)=\begin{bmatrix}
            e^{x-y}&-e^{x-y}\\
            1&-1
        \end{bmatrix}
    \end{equation*}
    Hence 
    \begin{align*}
        D(f\circ g)(1,1)&=\begin{bmatrix}
            1&-1\\
            2&0
        \end{bmatrix}\begin{bmatrix}
            1&-1\\
            1&-1
        \end{bmatrix}\\
        &=\begin{bmatrix}
            0&0\\
            2&-2
        \end{bmatrix}
    \end{align*}
\end{proof}






\begin{prob}[2.5, Q8]
    Let \( f(u, v, w) = (e^{u-w}, \cos (v + u) + \sin (u + v + w)) \) and \( g(x, y) = (e^x, \cos (y - x), e^{-y}). \)  
   Calculate \( f \circ g \) and \( D(f \circ g)(0, 0)\).
\end{prob}
\begin{proof}
    We have 
    \begin{equation*}
        f\circ g =(e^{e^x-\cos(y-x)}, \cos(e^x+\cos(y-x)), \sin(e^{x}+e^{-y}+\cos(y-x)))
    \end{equation*}
    and $g(0,0)=(1, 1, 1)$. Thus 
    \begin{equation*}
        D(f\circ g)(0,0)=Df(1,1,1)Dg(0,0)
    \end{equation*}
    where 
    \begin{equation*}
        Df(u,v,w)=\begin{bmatrix}
            e^{u-w}&0&-e^{u-w}\\
            -\sin(v+u)+\cos(u+v+w)&-\sin(v+u)+\cos(u+v+w)&\cos(u+v+w)
        \end{bmatrix}
    \end{equation*}
    and 
    \begin{equation*}
        Dg(x,y)=\begin{bmatrix}
            e^x&0\\
            \sin(y-x)&-\sin(y-x)\\
            0&-e^{-y}
        \end{bmatrix}
    \end{equation*}
    Thus 
    \begin{align*}
        D(f\circ g)(0,0)&=\begin{bmatrix}
            1&0&-1\\
            -\sin 2+\cos 3&-\sin 2+\cos 3&\cos 3
        \end{bmatrix}\begin{bmatrix}
            1&0\\
            0&0\\
            0&-1
        \end{bmatrix}\\
        &=\begin{bmatrix}
            1&1\\
            -\sin 2+\cos 3&-\cos 3
        \end{bmatrix}
    \end{align*}
\end{proof}


\chapter{Higher-Order Derivatives: Maxima and Minima}

\section*{\centering Week 7 (3/2-3/6)}


\begin{defn}[quadratic form]
    A function $g:\R^n\to\R$ is called a \textbf{quadratic form} if it is given by 
    \begin{equation*}
        g(h_1,\dots, h_n)=\sum_{i,j=1}^na_{ij}h_ih_j
    \end{equation*}
    where $(a_{ij})$ is an $n\times n$ matrix. We can also write $g$ as follows:
    \begin{equation*}
        g(h_1,\dots,h_n)=[h_1,\dots,h_n]\begin{bmatrix}
            a_{11}&\dots &a_{1n}\\
            \vdots&\ddots &\vdots\\
            a_{n_1}&\dots&a_{nn}
        \end{bmatrix}\begin{bmatrix}
            h_1\\
            \vdots\\
            h_n
        \end{bmatrix}
    \end{equation*}

\end{defn}

\begin{defn}[Hessian matrix]
    Let $f:U\subset\R^n\to\R$, and suppose all the second-order partial derivatives $\frac{\partial^2 f}{\partial x_i\partial x_j}$ exist, then the Hessian matrix of $f$ is the $n\times n$ matrix given by 
    \begin{equation*}
        Hf=\begin{bmatrix}
            \frac{\partial^2 f}{\partial x_1\partial x_1}&\dots&\frac{\partial^2f}{\partial x_1\partial x_n}\\
            \vdots&\ddots&\vdots\\
            \frac{\partial^2f}{\partial x_nx_1}&\dots&\frac{\partial^2f}{\partial x_n\partial x_n}
        \end{bmatrix}
    \end{equation*}
    The Hessian as a quadratic function is defined by 
    \begin{equation*}
        Hf(x)(h)=\frac{1}{2}\begin{bmatrix}
            h_1&\dots&h_n
        \end{bmatrix}Hf(x)\begin{bmatrix}
            h_1\\
            \dots\\
            h_n
        \end{bmatrix}
    \end{equation*}
    where $h=(h_1,\dots,h_n)$.
\end{defn}

\begin{defn}[degenerate/nondegenerate points]
    Let $f:U\subset\R^2\to\R$ be of $C^2$, let $(x_0,y_0)$ be a critical point. We define the \textbf{discriminant}, \boldmath $\mathcal{D}$,\unboldmath of the Hessian by
    \begin{equation*}
        \mathcal{D}=\det (Hf)=\left(\frac{\partial^2f}{\partial x^2}\right)\left(\frac{\partial^2f}{\partial y^2}\right)-\left(\frac{\partial^2f}{\partial x\partial y}\right)^2
    \end{equation*}
    If $\mathcal{D}\neq 0$, the critical point $(x_0,y_0)$ is called \textbf{nondegenerate}; if $\mathcal{D}=0$, the point $(x_0,y_0)$ is called \textbf{degenerate}.
\end{defn}

\begin{defn}[positive, negative-definite]
    A quadratic form $g:\R^n\to\R$ is called \textbf{positive-definite} if $g(h)\geq 0$ for all $h\in\R^n$ and $g(h)=0$ implies $h=0$. Similarly, $g$ is \textbf{negative-definite} if $g(h)\leq 0$ for all $h\in\R^n$ and $g(h)=0$ implies $h=0$. (The matrix is positive-definite iff it is symmetric $A^T=A$ and the eigenvalues are nonnegative).
\end{defn}


% \begin{defn}[global extremum]
%     Let $f:A\to\R$ be a function defined on $A\subset\R^2$ or $A\subset\R^3$. A point $x_0\in A$ is said to be an \textbf{absolute maximum} if $f(x_0)\geq f(x)$ for all $x\in A$. Similarly, $x_0$ is an \textbf{absolute minimum} if $f(x_0)\leq f(x)$ for all $x\in A$. 
% \end{defn}

\begin{defn}[bounded set]
    A set $A\subset\R^n$ is said to be \textbf{bounded} if there is a number $M>0$ such that $\|x\|\leq M$ for all $x\in A$. 
\end{defn}




\begin{prop}[extremums are critical points]
    Let $f:U\subset\R^n\to\R$ be differentiable, where $U$ is open. If $x_0$ is a local extremum, then $Df(x_0)=0$. 
\end{prop}


\begin{prop}[extremum]
    Let $f\colon U\subset\R^n\to\R$ be in $C^3$, and $x_0$ is a critical point of $f$. If the Hessian $Hf(x_0)$ is positive-definite, then $x_0$ is a local minimum of $f$; if $Hf(x_0)$ is negative-definite, then $x_0$ is a local maximum.
\end{prop}




\begin{prop}[local minimum]
    Let $f(x,y)$ be of $C^2$, and $U$ is open in $\R^2$. A point $(x_0,y_0)$ is a strict local \textbf{minimum} of $f$ if the following conditions hold:
    \begin{enumerate}
        \item \begin{equation*}
            \frac{\partial f}{\partial x}(x_0,y_0)=\frac{\partial f}{\partial y}(x_0,y_0)=0
        \end{equation*}
        \item \begin{equation*}
            \mathcal{D}(x_0,y_0)>0
        \end{equation*}
        where $\mathcal{D}$ is the \textbf{discriminant} of the Hessian, defined by 
        \begin{equation*}
            \mathcal{D}=\det (Hf)=\left(\frac{\partial^2 f}{\partial x^2}\right)\left(\frac{\partial^2 f}{\partial y^2}\right)-\left(\frac{\partial^2 f}{\partial x\partial y}\right)^2
        \end{equation*}
        where $Hf$ is the $2\times 2$ Hessian matrix.
        \item  \begin{equation*}
            \frac{\partial^2f}{\partial x^2}(x_0,y_0)>0
        \end{equation*}
    \end{enumerate}
    If $ \frac{\partial^2f}{\partial x^2}(x_0,y_0)<0$ in 3, then it becomes a local \textbf{maximum}.
\end{prop}


% \begin{prop}[local maximum]
%     Let $f(x,y)$ be of $C^2$, and $U$ is open in $\R^2$. A point $(x_0,y_0)$ is a strict local \textbf{maximum} of $f$ if the following conditions hold:
%     \begin{enumerate}
%         \item \begin{equation*}
%             \frac{\partial f}{\partial x}(x_0,y_0)=\frac{\partial f}{\partial y}(x_0,y_0)=0
%         \end{equation*}
%         \item \begin{equation*}
%             \mathcal{D}(x_0,y_0)>0
%         \end{equation*}
%         where $\mathcal{D}$ is the {discriminant} of the Hessian, defined above.
%         \item  \begin{equation*}
%             \frac{\partial^2f}{\partial x^2}(x_0,y_0)<0
%         \end{equation*}
%     \end{enumerate}
% \end{prop}

\begin{prop}[saddle points]
    Let $f(x,y):U\subset\R^2\to \R$ be of  $C^2$, if $\frac{\partial f}{\partial x}(x_0,y_0)=\frac{\partial f}{\partial y}(x_0,y_0)=0$, and $\mathcal{D}(x_0,y_0)<0$, where $\mathcal{D}$ is the discriminant, then the critical point $(x_0,y_0)$ is a saddle point, i.e., neither a maximum or a minimum.
\end{prop}


\begin{prop}[continuous functions attain extremum on closed bounded sets]
    Let $f:D\to\R$ be continuous, where $D$ is closed and bounded in $\R^n$. Then $f$ assumes its absolute maximum and absolute minimum values at some point $x_0, x_1\in D$.
\end{prop}


\begin{prob}
    Is the following matrix positive-definite?
    \begin{equation*}
        \begin{bmatrix}
            1&0\\
            0&-1
        \end{bmatrix}
    \end{equation*}
\end{prob}

\begin{proof}
    It is not! Consider the vector $(0,1)$, we have 
    \begin{equation*}
        [0, 1]
\begin{bmatrix}
        1&0\\
        0&-1
    \end{bmatrix}\begin{bmatrix}
        0\\
        1
    \end{bmatrix}
    =[0,1]\begin{bmatrix}
        0\\
        -1
    \end{bmatrix}=-1
\end{equation*}
\end{proof}
% \vspace{2.5in}

\begin{prob}
    Find the critical point of $f(x,y)=y+x\sin y$ and classify whether it is a local max/min or a saddle point.
\end{prob}
\begin{proof}
    We compute 
    \begin{equation*}
        f_x=\sin y, \quad f_y=1+x\cos y
    \end{equation*}
    Setting them both to $0$ gives 
    \begin{equation*}
        (1, n\pi), \text{ when $n$ is odd}, \quad (-1,n\pi) \text{ when $n$ is even}
    \end{equation*}
    Now we compute the discriminant:
    \begin{equation*}
        f_{xx}=0, \quad f_{xy}=f_{yx}=\cos y, \quad f_{yy}=-x\sin y
    \end{equation*}
    Thus 
    \begin{equation*}
        \mathcal{D}=\det\begin{bmatrix}
            0&\cos y\\
            \cos y&-x\sin y
        \end{bmatrix}=-\cos^2y
    \end{equation*}
    Thus $\mathcal{D}<0$ for all the critical points, hence they are saddle points!
\end{proof}


\newpage

\section*{\centering Week 8 (3/9-3/13)}

\begin{prop}
    If $f$ has a maximum or minimum
    at $x_0$ when constrained to a surface $S$, then $\nabla f(x_0)$ is perpendicular to $S$ at $x_0$.
\end{prop}
\begin{prop}
Let \( f, g : U \subset \mathbb{R}^n \to \mathbb{R} \) and \(\vec{x_0} \in U\) such that \( g({x_0}) = c \). Let \( \mathcal{L}_c \) be the level set for \( g \) with value \( c \) and assume  
\[
\nabla g(\vec{x_0}) \neq \vec{0}.
\] 
If \( f \) restricted to \( \mathcal{L}_c \) has a local minimum or maximum on \( \mathcal{L}_c \) at \( {x_0} \), then there exists \( \lambda \in \mathbb{R} \) such that  
\[
\nabla f({x_0}) = \lambda \nabla g({x_0}).
\]
\end{prop}


\begin{prob}[Marsden-Tromba, III. 2]
Let $f(x,y,z)=x-y+z$, find the extremum of $f$ subject to the constraint $x^2+y^2+z^2=2$.
\end{prob}
\begin{proof}
    We compute the gradient of $f$ and $g(x,y,z)=x^2+y^2+z^2$:
    \begin{equation*}
        \nabla f(x,y,z)=\begin{bmatrix}
            1&-1&1
        \end{bmatrix}\quad \nabla g(x,y,z)=\begin{bmatrix}
            2x&2y&2z
        \end{bmatrix}
    \end{equation*}
    By the proposition above, we need to have 
    \begin{align*}
        \lambda&=2x\\
        -\lambda&=2y\\
        \lambda&=2z
    \end{align*}
    Equating all $\lambda$ gives 
    \begin{equation*}
        x=z=-y
    \end{equation*}
    Plugging in the constraint we get 
    \begin{equation*}
        3x^2=2
    \end{equation*}
    Hence two critical points 
    \begin{equation*}
        \left(\sqrt{\frac{2}{3}}, -\sqrt{\frac{2}{3}}, \sqrt{\frac{2}{3}}\right), \quad \left(-\sqrt{\frac{2}{3}}, \sqrt{\frac{2}{3}}, -\sqrt{\frac{2}{3}}\right)
    \end{equation*}
    Plugging them in we find the extremums are $\sqrt{6}$ and $-\sqrt{6}$.
\end{proof}



\begin{prob}[Marsden-Tromba, III. 16]
Use Lagrange multipliers to find the distance from the point $(2, 0, -1)$ to the plane $3x - 2y + 8z + 1 = 0$.
\end{prob}
\begin{proof}
    Let $(x,y,z)$ be a point on the plane, then we would like the minimize the function 
    \begin{equation*}
        f(x,y,z)=(x-2)^2+y^2+(z+1)^2
    \end{equation*}
    with the constraint
    \begin{equation*}
        3x - 2y + 8z + 1 = 0
    \end{equation*}
    Writing $g(x,y,z)=3x - 2y + 8z + 1$, we do the exact same thing as we did above:
    \begin{equation*}
        \nabla f=\begin{bmatrix}
            2x-4&2y&2z+2
        \end{bmatrix}, \quad \nabla g=\begin{bmatrix}
            3&-2&8
        \end{bmatrix}
    \end{equation*}
    Then setting 
    \begin{align*}
        2x-4&=3\lambda\\
        2y&=-2\lambda\\
        2z+2&=8\lambda
    \end{align*}
    One can then replace $x,y,z$ with expressions in $\lambda$ in the constraint:
    \begin{equation*}
        3x-2y+8z+1=0
    \end{equation*}
    which gives 
    \begin{equation*}
        \lambda=2/77
    \end{equation*}
    Then plugging in $\lambda$ to solve for $x,y,z$, the $\sqrt{f(x,y,z)}$ is the final answer. (I am too lazy to do the computation).
\end{proof}



\begin{prob}
    Find the absolute maximum of $f(x,y)=2x^2y$ inside the disk $D=\{(x,y): x^2+y^2\leq 1\}$.
\end{prob}
\begin{proof}
    We first consider the points on the interior $\{(x,y): x^2+y^2<1\}$. We do so by finding the critical points $\nabla f(x,y)=0$.
    \begin{equation*}
        \nabla f(x,y)=\begin{bmatrix}4xy&2x^2\end{bmatrix}=0
    \end{equation*}
    which implies $(x,y)=(0,0)$. And $f(0,0)=0$.

    Now we consider the boundary. Let $g(x,y)=x^2+y^2$, using Lagrange, we set up 
    \begin{equation*}
        \nabla f=\lambda\nabla g\Rightarrow\begin{bmatrix}
            4xy&2x^2
        \end{bmatrix}=\lambda\begin{bmatrix}
            2x&2y
        \end{bmatrix}
    \end{equation*}
    This implies 
    \begin{equation*}
        \begin{cases}
            4xy=2\lambda x\\
            2x^2=2\lambda y
        \end{cases}\Rightarrow \begin{cases}
            2y=\lambda\\
            x^2=\lambda y
        \end{cases}, \quad x^2+y^2=1
    \end{equation*}
    This implies 
    \begin{equation*}
        (x,y)=\left(\frac{1}{\sqrt{3}}, \frac{\sqrt{2}}{\sqrt{3}}\right)
    \end{equation*}
    thus 
    \begin{equation*}
        f(x,y)=\frac{2\sqrt{6}}{9}
    \end{equation*}
    comparing it with $f(0,0)=0$, we see 
    \begin{equation*}
        \left(\frac{1}{\sqrt{3}}, \frac{\sqrt{2}}{\sqrt{3}}\right) \text{ is an absolute maximum.}
    \end{equation*}
\end{proof}


\chapter{Vector-Valued Functions}
\section*{\centering (Spring Break)}

% \begin{center}
%     \Large Calc III-Week 8 (Fall Break)
% \end{center}

\renewcommand\thesection{\arabic{section}}

\noindent
Topics: (1) Acceleration and Arc Length, (2) Vector Fields.

\begin{prop}[Newton's second law]
    Let $c(t)$ be a path of a particle with mass $m$ and $a(t)=c''(t)$ be the acceleration, then 
    \begin{equation*}
        F(c(t))=ma(t)
    \end{equation*}
    where $F$ is the force applying on the particle.
\end{prop}


\begin{defn}[arc length]
    Let $c(t)=(x(t), y(t), z(t))$ be a path, then the length of the path in $\R^3$ from $t_0\leq t\leq t_1$ is 
    \begin{align*}
        L_{t_0\to t_1}(c)&=\int_{t_0}^{t_1}\left(x'(t)^2+y'(t)^2+z'(t)^2\right)^\frac{1}{2}dt\\
        &=\int_{t_0}^{t_1}\|c'(t)\|dt
    \end{align*}
    More generally, if $c(t)=(x_1(t), \dots, x_n(t))$ is a path in $\R^n$, then 
    \begin{equation*}
        L_{t_0\to t_1}(c)=\int_{t_0}^{t_1}\left(\sum_{i=1}^nx_i'(t)^2\right)^\frac{1}{2}dt
    \end{equation*}
\end{defn}


\begin{defn}[vector field]
    A vector field is a function $F:A\subset\R^n\to\R^n$ that assigns $x\in\R^n$ to another vector $F(x)\in\R^n$.
\end{defn}







\begin{prob}
    Find the velocity, speed, and acceleration of the following path at $t=0$:
    \begin{equation*}
        c(t)=(\cos t, 2t, -\sin t)
    \end{equation*}
\end{prob}
\begin{proof}
    The velocity is 
    \begin{equation*}
        c'(t)=(-\sin t, 2, -\cos t), \quad c'(0)=(0,2,-1)
    \end{equation*}
    And the speed is 
    \begin{equation*}
        \|c'(t)\|=\sqrt{5}
    \end{equation*}
\end{proof}

\begin{prob}
    Find the length of the curve above from $t=0$ to $t=2$.
\end{prob}
\begin{proof}
    \begin{align*}
        L_{0\to 2}\|c'(t)\|dt&=\int_0^2\left(\sin^2t+4+\cos^2t\right)^\frac{1}{2}dt\\
        &=\int_0^2\sqrt{5}dt\\
        &=2\sqrt{5}
    \end{align*}
\end{proof}




\chapter{Double and Triple Integrals}

\section*{\centering Week 10 (10/27-31)}

% \begin{center}
%     \Large Calc III-Week 10 (10/27-31)
% \end{center}

% \renewcommand\thesection{\arabic{section}}

\noindent
Topics: (1) Divergence and Curl, (2) Double integrals.



\begin{defn}[flow line]
    Let ${F}$ be a vector field, a flow line of $F$ is a path $c(t)$ satisfying 
    \begin{equation*}
        c'(t)=F(c(t))
    \end{equation*}
    (Tangent vector of the path coincides with the given vector field ${F}$).
\end{defn}

\begin{defn}[divergence]
    Let ${F}$ be a vector field in $\R^3$ $F=(F_1,F_2,F_3)$, the divergence of ${F}$ is the \textbf{scalar field} (assigns one number to an given point $(x, y, z)$), 
    \begin{equation*}
        \diverg F\coloneq\nabla\cdot F=\frac{\partial F_1}{\partial x}+\frac{\partial F_2}{\partial y}+\frac{\partial F_3}{\partial z}
    \end{equation*}
    More generally, if $F=(F_1,\dots, F_n)$ is a vector field on $\R^n$, its divergence is 
    \begin{equation*}
        \diverg F=\sum_{i=1}^n\frac{\partial F_i}{\partial x_i}=\frac{\partial F_1}{\partial x_1}+\dots+\frac{\partial F_n}{\partial x_n}
    \end{equation*}
\end{defn}

\begin{remark}
    We write the divergence as $\nabla\cdot F$ because 
    \begin{equation*}
        \nabla=\left(\frac{\partial}{\partial x_1}, \dots, \frac{\partial}{\partial x_n}\right)
    \end{equation*}
    and if $F=(F_1,\dots, F_n)$, 
    \begin{equation*}
        \diverg F=\frac{\partial F_1}{\partial x_1}+\dots+\frac{\partial F_n}{\partial x_n}=\left(\frac{\partial}{\partial x_1}, \dots, \frac{\partial}{\partial x_n}\right)\cdot(F_1,\dots, F_n)=\nabla\cdot F
    \end{equation*}
\end{remark}


\begin{defn}[curl]
    Let $F$ be a vector field in $\R^3$, writing $F=(F_1,F_2,F_3)$, the \textbf{curl} of $F$ is the vector field 
    \begin{equation*}
        \curl F\coloneq\nabla\times F=\det\begin{bmatrix}
            i&j&k\\
            \frac{\partial}{\partial x}&\frac{\partial}{\partial y}&\frac{\partial}{\partial z}\\
            F_1&F_2&F_3
        \end{bmatrix}
    \end{equation*}
    If $\curl F=0$, then we say the vector field is \textbf{irrotational}.
\end{defn}
% \begin{warn}
%     Irrotational does not mean the vector field doesn't look like rotations.
% \end{warn}

\begin{prop}[gradient is irrotational]
    Let $f\in C^2$, viewing $\nabla f$ as a vector field, then
    \begin{equation*}
        \nabla\times(\nabla f)=0
    \end{equation*}    
\end{prop}

\begin{prop}[divergence of a curl vanishes]
    For any $C^2$ vector field $F$, 
    \begin{equation*}
        \nabla\cdot(\nabla\times F)=0
    \end{equation*}
\end{prop}



\newpage
\begin{prob}
    Show that the vector field $V(x,y,z)=(x^2, -y, z)$ is not the curl of any vector field $F$. In other words, there is no vector field $F$ such that 
    \begin{equation*}
        V=\curl F
    \end{equation*}
\end{prob}
% \begin{proof}
%     By the above proposition, if there exists $F$ such that 
%     \begin{equation*}
%         V=\curl F
%     \end{equation*}
%     then 
%     \begin{equation*}
%         \nabla\cdot V=0
%     \end{equation*}
%     However, 
%     \begin{equation*}
%         \nabla\cdot V(x,y,z)=2x\neq 0 \text{ if } x\neq 0
%     \end{equation*}
%     this is a contradiction, hence no such $F$ exists.
% \end{proof}

\vspace{8cm}


\begin{prob}[Marsden-Tromba, IV.4, 21]
    Let $F(x,y,z)=(x^2, x^2y, z+zx)$. Can there exist a function $f:\R^3\to\R$ such that $F=\nabla f$?
\end{prob}
% \begin{proof}
%     No. Suppose there exists such $f$, then the gradient must be irrotational. In other words, we must have 
%     \begin{equation*}
%         \nabla\times F=0
%     \end{equation*}
%     Thus we compute the curl of $F$:
%     \begin{equation*}
%         \nabla\times F=(-2yz, z, 0)
%     \end{equation*}
%     and it is not identically $0$.
% \end{proof}



\newpage


\begin{prop}[Fubini's Theorem for rectangles]
    Let $f$ be a continuous function on a rectangular domain $R=[a,b]\times[c,d]$, then 
    \begin{equation*}
        \int_a^b\int_c^df(x,y)dydx=\int_c^d\int_a^bf(x,y)dxdy
    \end{equation*}
\end{prop}

\begin{prop}[Fubini's Theorem for general regions]
    Suppose $D$ is a set of points $(x,y)$ such that $y\in [c,d]$ and $\psi_1(y)\leq x\leq\psi_2(y)$, and similarly for $x\in [a,b]$, $\varphi_1(x)\leq y\leq\varphi_2(x)$. If $f$ is continuous on $D$, then 
    \begin{equation*}
        \iint_Df(x,y)dA=\int_a^b\int_{\varphi_1(x)}^{\varphi_2(x)}f(x,y)dydx=\int_c^d\int_{\psi_1(y)}^{\psi_2(y)}f(x,y)dxdy
    \end{equation*}
\end{prop}
\begin{prob}
    Change the order of integration to $dydx$ for the following function:
    \begin{equation*}
        \int_0^1\int_{e^y}^{e}\frac{x}{\ln x}dxdy
    \end{equation*}
\end{prob}
\begin{proof}
    It should be 
    \begin{equation*}
        \int_1^e\int_{0}^{\ln x}\frac{x}{\ln x}dydx
    \end{equation*}
\end{proof}



\begin{prob}
    Change the order of integrations for the following functions:
    \begin{enumerate}
        \item \begin{equation*}
            \int_0^1\int_x^1f(x,y)dydx
        \end{equation*}
        \item \begin{equation*}
            \int_0^1\int_{-y}^{y^3}f(x,y)dxdy
        \end{equation*}
        \item \begin{equation*}
            \int_0^3\int_{2x}^6f(x,y)dydx
        \end{equation*}
        \item \begin{equation*}
            \int_0^1\int_{-\sqrt{y}}^{y^2}f(x,y)dxdy
        \end{equation*}
        \item \begin{equation*}
            \int_0^8\int_{\sqrt[3]{y}}^2f(x,y)dxdy
        \end{equation*}
        \item \begin{equation*}
            \int_0^1\int_{\ln y}^1f(x,y)dxdy
        \end{equation*}
    \end{enumerate}
\end{prob}
\begin{proof}
    \begin{enumerate}
        \item It should be 
        \begin{equation*}
            \int_0^1\int_0^yf(x,y)dxdy
        \end{equation*}
        \item It should be 
        \begin{equation*}
            \int_{-1}^0\int_{-x}^{1}f(x,y)dydx+\int_{0}^1\int_{\sqrt{x}}^1f(x,y)dydx
        \end{equation*}
        \item It should be 
        \begin{equation*}
            \int_0^6\int_0^{\frac{y}{2}}f(x,y)dxdy
        \end{equation*}
        \item It should be \begin{equation*}
            \int_0^1\int_{\sqrt{x}}^1f(x,y)dydx+\int_{-1}^0\int_{x^2}^1f(x,y)dydx
        \end{equation*}
        \item It should be 
        \begin{equation*}
            \int_0^2\int_0^{x^3}f(x,y)dydx
        \end{equation*}
        \item It should be 
        \begin{equation*}
            \int_{-\infty}^0\int_0^{e^x}f(x,y)dydx+\int_0^1\int_0^1f(x,y)dydx
        \end{equation*}
    \end{enumerate}
\end{proof}









\end{document}